\documentclass{article}
%To use pdflatex, uncomment these lines, as well as the \href lines
%in each entry
\usepackage[pdftex,
       colorlinks=true,
       urlcolor=blue,       % \href{...}{...} external (URL)
       filecolor=green,     % \href{...} local file
       linkcolor=red,       % \ref{...} and \pageref{...}
       pdftitle={Papers by Francesca Ricci-Tam},
       pdfauthor={Francesca Ricci-Tam},
       pdfsubject={Just a test},
       pdfkeywords={test testing testable},
       pagebackref,
       pdfpagemode=None,
        bookmarksopen=true]{hyperref}
%\usepackage{arial}
\renewcommand{\familydefault}{\sfdefault} % San serif
\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}

\pagestyle{empty}
\oddsidemargin 0.0in
\textwidth 6.5in
\topmargin -0.75in
\textheight 9.5in

\begin{document}
\title{Papers by Francesca Ricci-Tam}
\author{Francesca Ricci-Tam}
\date{\today}
\maketitle
\begin{enumerate}

%%   LIST OF PAPERS
%%   Please comment out anything between here and the
%%   first \item
%%   Please send any updates or corrections to the list to
%%   admin@inspirehep.net

%\cite{Khachatryan:2015oba}
\item%{Khachatryan:2015oba}
{\bf ``Search for vector-like charge 2/3 T quarks in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1509.04177 [hep-ex]
  
 %(Sep 14, 2015)
\href{http://inspirehep.net/record/1393276}{HEP entry}



%\cite{Khachatryan:2015hba}
\item%{Khachatryan:2015hba}
{\bf ``Measurement of the top quark mass using proton-proton data at sqrt(s) = 7 and 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1509.04044 [hep-ex]
  
 %(Sep 14, 2015)
\href{http://inspirehep.net/record/1393269}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015zaa}
\item%{Khachatryan:2015zaa}
{\bf ``Measurement of the inelastic cross section in proton-lead collisions at a centre-of-mass energy per nucleon pair of 5.02 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1509.03893 [hep-ex]
  
 %(Sep 13, 2015)
\href{http://inspirehep.net/record/1393261}{HEP entry}



%\cite{Khachatryan:2015qda}
\item%{Khachatryan:2015qda}
{\bf ``Search for single production of scalar leptoquarks in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1509.03750 [hep-ex]
  
 %(Sep 12, 2015)
\href{http://inspirehep.net/record/1393258}{HEP entry}



%\cite{Khachatryan:2015vaa}
\item%{Khachatryan:2015vaa}
{\bf ``Search for pair production of first and second generation leptoquarks in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1509.03744 [hep-ex]
  
 %(Sep 12, 2015)
\href{http://inspirehep.net/record/1393257}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015rxa}
\item%{Khachatryan:2015rxa}
{\bf ``Measurement of differential cross sections for Higgs boson production in the diphoton decay channel in pp collisions at $\sqrt{s}$=8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.07819 [hep-ex]
  
 %(Aug 31, 2015)
\href{http://inspirehep.net/record/1391147}{HEP entry}
%3 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015qxa}
\item%{Khachatryan:2015qxa}
{\bf ``Search for a charged Higgs boson in pp collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.07774 [hep-ex]
  
 %(Aug 31, 2015)
\href{http://inspirehep.net/record/1391146}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015kxa}
\item%{Khachatryan:2015kxa}
{\bf ``Search for supersymmetry in the vector-boson fusion topology in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.07628 [hep-ex]
  
 %(Aug 30, 2015)
\href{http://inspirehep.net/record/1391140}{HEP entry}



%\cite{Khachatryan:2015uja}
\item%{Khachatryan:2015uja}
{\bf ``Study of B meson production in pPb collisions at $\sqrt{s_{ \rm{NN}}} =$ = 5.02 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.06678 [nucl-ex]
  
 %(Aug 26, 2015)
\href{http://inspirehep.net/record/1390110}{HEP entry}



%\cite{Khachatryan:2015pua}
\item%{Khachatryan:2015pua}
{\bf ``Search for W' decaying to tau lepton and neutrino in proton-proton collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.04308 [hep-ex]
  
 %(Aug 18, 2015)
\href{http://inspirehep.net/record/1388363}{HEP entry}



%\cite{Khachatryan:2015mna}
\item%{Khachatryan:2015mna}
{\bf ``Measurement of the charge asymmetry in top quark pair production in pp collisions at $\sqrt{s}$ = 8 TeV using a template method''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.03862 [hep-ex]
  
 %(Aug 16, 2015)
\href{http://inspirehep.net/record/1388178}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2015ooa}
\item%{CMS:2015ooa}
{\bf ``Search for neutral MSSM Higgs bosons decaying to $\mu^{+} \mu^{-}$ in pp collisions at $ \sqrt{s} =$ 7 and 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.01437 [hep-ex]
  
 %(Aug 6, 2015)
\href{http://inspirehep.net/record/1386854}{HEP entry}



%\cite{CMS:2015loa}
\item%{CMS:2015loa}
{\bf ``Search for supersymmetry with a photon, a lepton, and missing transverse momentum in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1508.01218 [hep-ex]
  
 %(Aug 5, 2015)
\href{http://inspirehep.net/record/1386851}{HEP entry}



%\cite{Khachatryan:2015isa}
\item%{Khachatryan:2015isa}
{\bf ``Angular analysis of the decay $ \mathrm{ B^0 \to K^{*0} \mu^{+} \mu^{-}  }$ from pp collisions at $\sqrt{s}=  $ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.08126 [hep-ex]
  
 %(Jul 29, 2015)
\href{http://inspirehep.net/record/1385600}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015nza}
\item%{Khachatryan:2015nza}
{\bf ``Measurement of the CP-violating weak phase $\mathrm{ \phi_s }$ and the decay width difference $ \Delta \Gamma_{ \mathrm{s} }$ using the $ \mathrm{B^0_s} \to \mathrm{J} / \psi \phi(1020) $ decay channel in pp collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.07527 [hep-ex]
  
 %(Jul 27, 2015)
\href{http://inspirehep.net/record/1385111}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015jza}
\item%{Khachatryan:2015jza}
{\bf ``Measurement of the underlying event activity using charged-particle jets in proton-proton collisions at $\sqrt{s}$ = 2.76 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.07229 [hep-ex]
  
 %(Jul 26, 2015)
\href{http://inspirehep.net/record/1385107}{HEP entry}



%\cite{Khachatryan:2015gza}
\item%{Khachatryan:2015gza}
{\bf ``Search for pair-produced vector-like B quarks in proton-proton collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.07129 [hep-ex]
  
 %(Jul 25, 2015)
\href{http://inspirehep.net/record/1385104}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015mma}
\item%{Khachatryan:2015mma}
{\bf ``Limits on the Higgs boson lifetime and width from its decay to four charged leptons''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.06656 [hep-ex]
  
 %(Jul 23, 2015)
\href{http://inspirehep.net/record/1384772}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015jna}
\item%{Khachatryan:2015jna}
{\bf ``Pseudorapidity distribution of charged hadrons in proton-proton collisions at $\sqrt{s}$ = 13 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.05915 [hep-ex]
  
 %(Jul 21, 2015)
\href{http://inspirehep.net/record/1384119}{HEP entry}



%\cite{Khachatryan:2015sga}
\item%{Khachatryan:2015sga}
{\bf ``Measurement of the $W^+W^-$ cross section in pp collisions at $\sqrt{s}$ = 8 TeV and limits on anomalous gauge couplings''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.03268 [hep-ex]
  
 %(Jul 12, 2015)
\href{http://inspirehep.net/record/1382594}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015oga}
\item%{Khachatryan:2015oga}
{\bf ``Inclusive and differential measurements of the $\mathrm{ t \bar{t} }$ charge asymmetry in pp collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.03119 [hep-ex]
  
 %(Jul 11, 2015)
\href{http://inspirehep.net/record/1382590}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015lga}
\item%{Khachatryan:2015lga}
{\bf ``Search for a Higgs boson decaying into $\gamma^*\gamma\to\ell\ell\gamma$ with low dilepton mass in pp collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.03031 [hep-ex]
  
 %(Jul 10, 2015)
\href{http://inspirehep.net/record/1382587}{HEP entry}



%\cite{Khachatryan:2015exa}
\item%{Khachatryan:2015exa}
{\bf ``Search for supersymmetry with photons in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.02898 [hep-ex]
  
 %(Jul 10, 2015)
\href{http://inspirehep.net/record/1382346}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015vta}
\item%{Khachatryan:2015vta}
{\bf ``Search for exotic decays of a Higgs boson into undetectable particles and photons''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.00359 [hep-ex]
  
 %(Jul 1, 2015)
\href{http://inspirehep.net/record/1380907}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015fia}
\item%{Khachatryan:2015fia}
{\bf ``Production of leading charged particles and leading charged-particle jets at small transverse momenta in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1507.00233 [hep-ex]
  
 %(Jul 1, 2015)
\href{http://inspirehep.net/record/1380605}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015tra}
\item%{Khachatryan:2015tra}
{\bf ``Search for Neutral MSSM Higgs Bosons Decaying into A Pair of Bottom Quarks''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.08329 [hep-ex]
  
 %(Jun 27, 2015)
\href{http://inspirehep.net/record/1380177}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015sma}
\item%{Khachatryan:2015sma}
{\bf ``Search for Resonant $\mathrm{t\bar{t}}$ Production in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.03062 [hep-ex]
  
 %(Jun 9, 2015)
\href{http://inspirehep.net/record/1375314}{HEP entry}
%10 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015qba}
\item%{Khachatryan:2015qba}
{\bf ``Search for Diphoton Resonances in the Mass Range from 150 to 850 GeV in pp Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.02301 [hep-ex]
  
 %(Jun 7, 2015)
\href{http://inspirehep.net/record/1375026}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015bma}
\item%{Khachatryan:2015bma}
{\bf ``Search for A Massive Resonance Decaying into a Higgs Boson and a W or Z Boson in Hadronic Final States in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.01443 [hep-ex]
  
 %(Jun 3, 2015)
\href{http://inspirehep.net/record/1374621}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015bnx}
\item%{Khachatryan:2015bnx}
{\bf ``Search for the standard model Higgs boson produced through vector boson fusion and decaying to $b \overline{b}$''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.01010 [hep-ex]
    \\{}10.1103/PhysRevD.92.032008
\\{}Phys.\ Rev.\ D {\bf 92}, no. 3, 032008 (2015) %(Jun 2, 2015)
\href{http://inspirehep.net/record/1374219}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015wka}
\item%{Khachatryan:2015wka}
{\bf ``A Search for Pair Production of New Light Bosons Decaying into Muons''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1506.00424 [hep-ex]
  
 %(Jun 1, 2015)
\href{http://inspirehep.net/record/1373914}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015jea}
\item%{Khachatryan:2015jea}
{\bf ``Search for Neutral Color-Octet Weak-Triplet Scalar Particles in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1505.08118 [hep-ex]
  
 %(May 29, 2015)
\href{http://inspirehep.net/record/1373745}{HEP entry}



%\cite{Khachatryan:2015ira}
\item%{Khachatryan:2015ira}
{\bf ``Comparison of the Z$/\gamma^{*}$ + Jets to $\gamma$ + Jets Cross Sections in pp Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1505.06520 [hep-ex]
  
 %(May 24, 2015)
\href{http://inspirehep.net/record/1372730}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015oqa}
\item%{Khachatryan:2015oqa}
{\bf ``Measurement of the Differential Cross Section for Top Quark Pair Production in pp Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1505.04480 [hep-ex]
  
 %(May 17, 2015)
\href{http://inspirehep.net/record/1370682}{HEP entry}
%23 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015lba}
\item%{Khachatryan:2015lba}
{\bf ``Search for a pseudoscalar boson decaying into a Z boson and the 125 GeV Higgs boson in $ℓ^+ℓ^−b\overline{b}$ final states''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1504.04710 [hep-ex]
    \\{}10.1016/j.physletb.2015.07.010
\\{}Phys.\ Lett.\ B {\bf 748}, 221 (2015) %(Apr 18, 2015)
\href{http://inspirehep.net/record/1362177}{HEP entry}
%5 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015paa}
\item%{Khachatryan:2015paa}
{\bf ``Angular coefficients of Z bosons produced in pp collisions at sqrt(s) = 8 TeV and decaying to mu+mu- as a function of transverse momentum and rapidity''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1504.03512 [hep-ex]
    \\{}10.1016/j.physletb.2015.08.061
\\{}Phys.\ Rev.\ B {\bf 750}, 154 (2015) %(Apr 14, 2015)
\href{http://inspirehep.net/record/1359451}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015oaa}
\item%{Khachatryan:2015oaa}
{\bf ``Measurement of the Z boson differential cross section in transverse momentum and rapidity in proton–proton collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1504.03511 [hep-ex]
    \\{}10.1016/j.physletb.2015.07.065
\\{}Phys.\ Lett.\ B {\bf 749}, 187 (2015) %(Apr 14, 2015)
\href{http://inspirehep.net/record/1359450}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015nua}
\item%{Khachatryan:2015nua}
{\bf ``Search for the production of dark matter in association with top-quark pairs in the single-lepton final state in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1504.03198 [hep-ex]
    \\{}10.1007/JHEP06(2015)121
\\{}JHEP {\bf 1506}, 121 (2015) %(Apr 13, 2015)
\href{http://inspirehep.net/record/1359293}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015cwa}
\item%{Khachatryan:2015cwa}
{\bf ``Search for a Higgs Boson in the Mass Range from 145 to 1000 GeV Decaying to a Pair of W or Z Bosons''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1504.00936 [hep-ex]
  
 %(Apr 3, 2015)
\href{http://inspirehep.net/record/1357982}{HEP entry}
%25 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015bsa}
\item%{Khachatryan:2015bsa}
{\bf ``Search for Third-Generation Scalar Leptoquarks in the t$\tau$ Channel in Proton-Proton Collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.09049 [hep-ex]
    \\{}10.1007/JHEP07(2015)042
\\{}JHEP {\bf 1507}, 042 (2015) %(Mar 31, 2015)
\href{http://inspirehep.net/record/1357201}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015gka}
\item%{Khachatryan:2015gka}
{\bf ``Measurement of diffraction dissociation cross sections in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.08689 [hep-ex]
    \\{}10.1103/PhysRevD.92.012003
\\{}Phys.\ Rev.\ D {\bf 92}, no. 1, 012003 (2015) %(Mar 30, 2015)
\href{http://inspirehep.net/record/1356998}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015wza}
\item%{Khachatryan:2015wza}
{\bf ``Searches for third-generation squark production in fully hadronic final states in proton-proton collisions at $ \sqrt{s} = 8$ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.08037 [hep-ex]
    \\{}10.1007/JHEP06(2015)116
\\{}JHEP {\bf 1506}, 116 (2015) %(Mar 27, 2015)
\href{http://inspirehep.net/record/1356728}{HEP entry}
%20 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Aad:2015zhl}
\item%{Aad:2015zhl}
{\bf ``Combined Measurement of the Higgs Boson Mass in $pp$ Collisions at $\sqrt{s}=7$ and 8 TeV with the ATLAS and CMS Experiments''}
  \\{}G.~Aad {\it et al.} [ATLAS and CMS Collaborations].
  \\{}arXiv:1503.07589 [hep-ex]
    \\{}10.1103/PhysRevLett.114.191803
\\{}Phys.\ Rev.\ Lett.\  {\bf 114}, 191803 (2015) %(Mar 26, 2015)
\href{http://inspirehep.net/record/1356276}{HEP entry}
%150 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015hha}
\item%{Khachatryan:2015hha}
{\bf ``Study of W boson production in pPb collisions at $\sqrt{s_{\mathrm{NN}}}$ = 5.02 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.05825 [nucl-ex]
  
 %(Mar 19, 2015)
\href{http://inspirehep.net/record/1353541}{HEP entry}
%6 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015pba}
\item%{Khachatryan:2015pba}
{\bf ``Measurements of the $ZZ$ production cross sections in the $2\ell2\nu$ channel in proton-proton collisions at $\sqrt{s}$ = 7 and 8 TeV and combined constraints on triple gauge couplings''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.05467 [hep-ex]
  
 %(Mar 18, 2015)
\href{http://inspirehep.net/record/1353393}{HEP entry}
%1 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015yea}
\item%{Khachatryan:2015yea}
{\bf ``Search for resonant pair production of Higgs bosons decaying to two bottom quark–antiquark pairs in proton–proton collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.04114 [hep-ex]
    \\{}10.1016/j.physletb.2015.08.047
\\{}Phys.\ Lett.\ B {\bf 749}, 560 (2015) %(Mar 13, 2015)
\href{http://inspirehep.net/record/1352128}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015axa}
\item%{Khachatryan:2015axa}
{\bf ``Search for vector-like T quarks decaying to top quarks and Higgs bosons in the all-hadronic channel using jet substructure''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.01952 [hep-ex]
    \\{}10.1007/JHEP06(2015)080
\\{}JHEP {\bf 1506}, 080 (2015) %(Mar 6, 2015)
\href{http://inspirehep.net/record/1348542}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015oea}
\item%{Khachatryan:2015oea}
{\bf ``Evidence for transverse momentum and pseudorapidity dependent event plane fluctuations in PbPb and pPb collisions''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1503.01692 [nucl-ex]
  
 %(Mar 5, 2015)
\href{http://inspirehep.net/record/1347386}{HEP entry}
%5 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015rja}
\item%{Khachatryan:2015rja}
{\bf ``Study of final-state radiation in decays of Z bosons produced in $pp$ collisions at 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.07940 [hep-ex]
    \\{}10.1103/PhysRevD.91.092012
\\{}Phys.\ Rev.\ D {\bf 91}, no. 9, 092012 (2015) %(Feb 27, 2015)
\href{http://inspirehep.net/record/1346843}{HEP entry}



%\cite{Khachatryan:2015kon}
\item%{Khachatryan:2015kon}
{\bf ``Search for lepton-flavour-violating decays of the Higgs boson''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.07400 [hep-ex]
    \\{}10.1016/j.physletb.2015.07.053
\\{}Phys.\ Lett.\ B {\bf 749}, 337 (2015) %(Feb 25, 2015)
\href{http://inspirehep.net/record/1346512}{HEP entry}
%43 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015lwa}
\item%{Khachatryan:2015lwa}
{\bf ``Search for physics beyond the standard model in events with two leptons, jets, and missing transverse momentum in pp collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.06031 [hep-ex]
    \\{}10.1007/JHEP04(2015)124
\\{}JHEP {\bf 1504}, 124 (2015) %(Feb 20, 2015)
\href{http://inspirehep.net/record/1345823}{HEP entry}
%31 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015kea}
\item%{Khachatryan:2015kea}
{\bf ``Measurement of the Zγ production cross section in pp collisions at 8 TeV and search for anomalous triple gauge boson couplings''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.05664 [hep-ex]
    \\{}10.1007/JHEP04(2015)164
\\{}JHEP {\bf 1504}, 164 (2015) %(Feb 19, 2015)
\href{http://inspirehep.net/record/1345354}{HEP entry}
%3 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015xaa}
\item%{Khachatryan:2015xaa}
{\bf ``Nuclear effects on the transverse momentum spectra of charged particles in pPb collisions at $\sqrt{s_{_\mathrm {NN}}} =5.02$ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.05387 [nucl-ex]
    \\{}10.1140/epjc/s10052-015-3435-4
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 5, 237 (2015) %(Feb 18, 2015)
\href{http://inspirehep.net/record/1345263}{HEP entry}
%6 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015waa}
\item%{Khachatryan:2015waa}
{\bf ``Evidence for Collective Multiparticle Correlations in p-Pb Collisions''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.05382 [nucl-ex]
    \\{}10.1103/PhysRevLett.115.012301
\\{}Phys.\ Rev.\ Lett.\  {\bf 115}, no. 1, 012301 (2015) %(Feb 18, 2015)
\href{http://inspirehep.net/record/1345262}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015ywa}
\item%{Khachatryan:2015ywa}
{\bf ``Search for narrow high-mass resonances in proton–proton collisions at $\sqrt{s}$ = 8 TeV decaying to a Z and a Higgs boson''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.04994 [hep-ex]
    \\{}10.1016/j.physletb.2015.07.011
\\{}Phys.\ Lett.\ B {\bf 748}, 255 (2015) %(Feb 17, 2015)
\href{http://inspirehep.net/record/1345160}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015xwa}
\item%{Khachatryan:2015xwa}
{\bf ``Distributions of topological observables in inclusive three- and four-jet events in pp collisions at sqrt(s) = 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.04785 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3491-9
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 7, 302 (2015) %(Feb 16, 2015)
\href{http://inspirehep.net/record/1345159}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015vra}
\item%{Khachatryan:2015vra}
{\bf ``Searches for supersymmetry using the M$_{T2}$ variable in hadronic events produced in pp collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.04358 [hep-ex]
    \\{}10.1007/JHEP05(2015)078
\\{}JHEP {\bf 1505}, 078 (2015) %(Feb 15, 2015)
\href{http://inspirehep.net/record/1345027}{HEP entry}
%27 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015rra}
\item%{Khachatryan:2015rra}
{\bf ``Measurement of J/ψ and ψ(2S) Prompt Double-Differential Cross Sections in pp Collisions at $\sqrt{s}$=7  TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.04155 [hep-ex]
    \\{}10.1103/PhysRevLett.114.191802
\\{}Phys.\ Rev.\ Lett.\  {\bf 114}, no. 19, 191802 (2015) %(Feb 13, 2015)
\href{http://inspirehep.net/record/1345023}{HEP entry}
%5 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015iwa}
\item%{Khachatryan:2015iwa}
{\bf ``Performance of photon reconstruction and identification with the CMS detector in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.02702 [physics.ins-det]
    \\{}10.1088/1748-0221/10/08/P08010
\\{}JINST {\bf 10}, no. 08, P08010 (2015) %(Feb 9, 2015)
\href{http://inspirehep.net/record/1343792}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015hwa}
\item%{Khachatryan:2015hwa}
{\bf ``Performance of electron reconstruction and selection with the CMS detector in proton-proton collisions at √s = 8  TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.02701 [physics.ins-det]
    \\{}10.1088/1748-0221/10/06/P06005
\\{}JINST {\bf 10}, no. 06, P06005 (2015) %(Feb 9, 2015)
\href{http://inspirehep.net/record/1343791}{HEP entry}
%57 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015lla}
\item%{Khachatryan:2015lla}
{\bf ``Constraints on the pMSSM, AMSB model and on other models from the search for long-lived charged particles in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.02522 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3533-3
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 7, 325 (2015) %(Feb 9, 2015)
\href{http://inspirehep.net/record/1343509}{HEP entry}
%6 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015ila}
\item%{Khachatryan:2015ila}
{\bf ``Search for a standard model Higgs boson produced in association with a top-quark pair and decaying to bottom quarks using a matrix element method''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.02485 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3454-1
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 6, 251 (2015) %(Feb 9, 2015)
\href{http://inspirehep.net/record/1343506}{HEP entry}
%21 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015pwa}
\item%{Khachatryan:2015pwa}
{\bf ``Search for supersymmetry using razor variables in events with $b$-tagged jets in $pp$ collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1502.00300 [hep-ex]
    \\{}10.1103/PhysRevD.91.052018
\\{}Phys.\ Rev.\ D {\bf 91}, 052018 (2015) %(Feb 1, 2015)
\href{http://inspirehep.net/record/1342447}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015qpa}
\item%{Khachatryan:2015qpa}
{\bf ``Measurements of the $\Upsilon$(1S), $\Upsilon$(2S), and $\Upsilon$(3S) differential cross sections in pp collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1501.07750 [hep-ex]
    \\{}10.1016/j.physletb.2015.07.037
\\{}Phys.\ Lett.\ B {\bf 749}, 14 (2015) %(Jan 30, 2015)
\href{http://inspirehep.net/record/1342266}{HEP entry}
%5 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015lua}
\item%{Khachatryan:2015lua}
{\bf ``Measurement of the ratio $\mathcal{B}( \mathrm{B}^0_{s} \to \mathrm{J}/\psi\, \mathrm{f}_0(980))/\mathcal{B}(\mathrm{B}^0_{s} \to \mathrm{J}/\psi\, \phi(1020))$ in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1501.06089 [hep-ex]
  
 %(Jan 24, 2015)
\href{http://inspirehep.net/record/1341039}{HEP entry}



%\cite{Khachatryan:2015jha}
\item%{Khachatryan:2015jha}
{\bf ``Search for decays of stopped long-lived particles produced in proton–proton collisions at $\sqrt{s}= 8\,\text {TeV} $''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1501.0560 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3367-z
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 4, 151 (2015) %(Jan 22, 2015)
\href{http://inspirehep.net/record/1340699}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015gha}
\item%{Khachatryan:2015gha}
{\bf ``Search for heavy Majorana neutrinos in $\mu^\pm \mu^\pm+$ jets events in proton-proton collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1501.05566 [hep-ex]
    \\{}10.1016/j.physletb.2015.06.070
\\{}Phys.\ Lett.\ B {\bf 748}, 144 (2015) %(Jan 22, 2015)
\href{http://inspirehep.net/record/1340696}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2015sja}
\item%{Khachatryan:2015sja}
{\bf ``Search for resonances and quantum black holes using dijet mass spectra in proton-proton collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1501.04198 [hep-ex]
    \\{}10.1103/PhysRevD.91.052009
\\{}Phys.\ Rev.\ D {\bf 91}, no. 5, 052009 (2015) %(Jan 17, 2015)
\href{http://inspirehep.net/record/1340084}{HEP entry}
%55 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014jba}
\item%{Khachatryan:2014jba}
{\bf ``Precise determination of the mass of the Higgs boson and tests of compatibility of its couplings with the standard model predictions using proton collisions at 7 and 8 $\,\text {TeV}$''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.8662 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3351-7
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 5, 212 (2015) %(Dec 30, 2014)
\href{http://inspirehep.net/record/1335811}{HEP entry}
%189 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014lpa}
\item%{Khachatryan:2014lpa}
{\bf ``Search for pair-produced resonances decaying to jet pairs in proton–proton collisions at $\sqrt{s}$=8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.7706 [hep-ex]
    \\{}10.1016/j.physletb.2015.04.045
\\{}Phys.\ Lett.\ B {\bf 747}, 98 (2015) %(Dec 24, 2014)
\href{http://inspirehep.net/record/1335501}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014fba}
\item%{Khachatryan:2014fba}
{\bf ``Search for physics beyond the standard model in dilepton mass spectra in proton-proton collisions at $ \sqrt{s}=8 $ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.6302 [hep-ex]
    \\{}10.1007/JHEP04(2015)025
\\{}JHEP {\bf 1504}, 025 (2015) %(Dec 19, 2014)
\href{http://inspirehep.net/record/1335131}{HEP entry}
%51 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014dpa}
\item%{CMS:2014dpa}
{\bf ``Searches for supersymmetry based on events with b jets and four W bosons in pp collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.4109 [hep-ex]
    \\{}10.1016/j.physletb.2015.04.002
\\{}Phys.\ Lett.\ B {\bf 745}, 5 (2015) %(Dec 12, 2014)
\href{http://inspirehep.net/record/1334141}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014mna}
\item%{CMS:2014mna}
{\bf ``Measurement of the inclusive 3-jet production differential cross section in proton–proton collisions at 7 TeV and determination of the strong coupling constant in the TeV range''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.1633 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3376-y
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 5, 186 (2015) %(Dec 4, 2014)
\href{http://inspirehep.net/record/1332746}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014jea}
\item%{CMS:2014jea}
{\bf ``Measurements of differential and double-differential Drell-Yan cross sections in proton-proton collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1412.1115 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3364-2
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 4, 147 (2015) %(Dec 2, 2014)
\href{http://inspirehep.net/record/1332509}{HEP entry}
%8 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014exa}
\item%{CMS:2014exa}
{\bf ``Search for stealth supersymmetry in events with jets, either photons or leptons, and low missing transverse momentum in pp collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.7255 [hep-ex]
    \\{}10.1016/j.physletb.2015.03.017
\\{}Phys.\ Lett.\ B {\bf 743}, 503 (2015) %(Nov 26, 2014)
\href{http://inspirehep.net/record/1330294}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014hka}
\item%{CMS:2014hka}
{\bf ``Search for long-lived particles that decay into final states containing two electrons or two muons in proton-proton collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.6977 [hep-ex]
    \\{}10.1103/PhysRevD.91.052012
\\{}Phys.\ Rev.\ D {\bf 91}, no. 5, 052012 (2015) %(Nov 25, 2014)
\href{http://inspirehep.net/record/1329959}{HEP entry}
%17 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014wda}
\item%{CMS:2014wda}
{\bf ``Search for long-lived neutral particles decaying to quark-antiquark pairs in proton-proton collisions at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.6530 [hep-ex]
    \\{}10.1103/PhysRevD.91.012007
\\{}Phys.\ Rev.\ D {\bf 91}, no. 1, 012007 (2015) %(Nov 24, 2014)
\href{http://inspirehep.net/record/1329792}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014gxa}
\item%{CMS:2014gxa}
{\bf ``Search for disappearing tracks in proton-proton collisions at $ \sqrt{s}=8 $ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.6006 [hep-ex]
    \\{}10.1007/JHEP01(2015)096
\\{}JHEP {\bf 1501}, 096 (2015) %(Nov 21, 2014)
\href{http://inspirehep.net/record/1329620}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014yxa}
\item%{CMS:2014yxa}
{\bf ``Measurement of the cross section ratio $\sigma_\mathrm{t \bar{t} b \bar{b}} / \sigma_\mathrm{t \bar{t}  jj }$ in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.5621 [hep-ex]
    \\{}10.1016/j.physletb.2015.04.060
\\{}Phys.\ Lett.\ B {\bf 746}, 132 (2015) %(Nov 20, 2014)
\href{http://inspirehep.net/record/1328962}{HEP entry}
%5 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014xfa}
\item%{CMS:2014xfa}
{\bf ``Observation of the rare $B^0_s\to\mu^+\mu^-$ decay from the combined analysis of CMS and LHCb data''}
  \\{}V.~Khachatryan {\it et al.} [CMS and LHCb Collaborations].
  \\{}arXiv:1411.4413 [hep-ex]
    \\{}10.1038/nature14474
\\{}Nature {\bf 522}, 68 (2015) %(Nov 17, 2014)
\href{http://inspirehep.net/record/1328493}{HEP entry}
%74 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014kca}
\item%{Khachatryan:2014kca}
{\bf ``Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.3441 [hep-ex]
    \\{}10.1103/PhysRevD.92.012004
\\{}Phys.\ Rev.\ D {\bf 92}, no. 1, 012004 (2015) %(Nov 12, 2014)
\href{http://inspirehep.net/record/1327726}{HEP entry}
%65 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014cja}
\item%{Khachatryan:2014cja}
{\bf ``Search for quark contact interactions and extra spatial dimensions using dijet angular distributions in proton–proton collisions at $\sqrt s =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.2646 [hep-ex]
    \\{}10.1016/j.physletb.2015.04.042
\\{}Phys.\ Lett.\ B {\bf 746}, 79 (2015) %(Nov 10, 2014)
\href{http://inspirehep.net/record/1327224}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014gga}
\item%{Khachatryan:2014gga}
{\bf ``Performance of the CMS missing transverse momentum reconstruction in pp data at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1411.0511 [physics.ins-det]
    \\{}10.1088/1748-0221/10/02/P02006
\\{}JINST {\bf 10}, no. 02, P02006 (2015) %(Nov 3, 2014)
\href{http://inspirehep.net/record/1325798}{HEP entry}
%15 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014rwa}
\item%{Khachatryan:2014rwa}
{\bf ``Search for new phenomena in monophoton final states in proton-proton collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.8812 [hep-ex]
  
 %(Oct 31, 2014)
\href{http://inspirehep.net/record/1325549}{HEP entry}
%28 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014waa}
\item%{Khachatryan:2014waa}
{\bf ``Constraints on parton distribution functions and extraction of the strong coupling constant from the inclusive jet cross section in pp collisions at $\sqrt{s} = 7$ $\,\text {TeV}$''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.6765 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3499-1
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 6, 288 (2015) %(Oct 24, 2014)
\href{http://inspirehep.net/record/1323630}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014aep}
\item%{Khachatryan:2014aep}
{\bf ``Search for a standard model-like Higgs boson in the $μ^+μ^−$ and $e^+e^−$ decay channels at the LHC''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.6679 [hep-ex]
    \\{}10.1016/j.physletb.2015.03.048
\\{}Phys.\ Lett.\ B {\bf 744}, 184 (2015) %(Oct 24, 2014)
\href{http://inspirehep.net/record/1323624}{HEP entry}
%29 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014sta}
\item%{Khachatryan:2014sta}
{\bf ``Study of vector boson scattering and search for new physics in events with two same-sign leptons and two jets''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.6315 [hep-ex]
    \\{}10.1103/PhysRevLett.114.051801
\\{}Phys.\ Rev.\ Lett.\  {\bf 114}, no. 5, 051801 (2015) %(Oct 23, 2014)
\href{http://inspirehep.net/record/1323444}{HEP entry}
%13 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014nfa}
\item%{Khachatryan:2014nfa}
{\bf ``Measurement of the ratio of the production cross sections times branching fractions of $B_{c}^{\pm} \to J/\psi \pi^{\pm}$ and $B^{\pm} \to J/\psi K^{\pm}$ and $\mathcal{B}(B_{c}^{\pm} \to J/\psi \pi^{\pm}\pi^{\pm}\pi^{\mp})/\mathcal{B}(B_{c}^{\pm} \to J/\psi \pi^{\pm})$ in pp collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.5729 [hep-ex]
    \\{}10.1007/JHEP01(2015)063
\\{}JHEP {\bf 1501}, 063 (2015) %(Oct 21, 2014)
\href{http://inspirehep.net/record/1323075}{HEP entry}
%2 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014csa}
\item%{Chatrchyan:2014csa}
{\bf ``Study of Z production in PbPb and pp collisions at $ \sqrt{s_{\mathrm{NN}}}=2.76 $ TeV in the dimuon and dielectron decay channels''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.4825 [nucl-ex]
    \\{}10.1007/JHEP03(2015)022
\\{}JHEP {\bf 1503}, 022 (2015) %(Oct 17, 2014)
\href{http://inspirehep.net/record/1322726}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014vla}
\item%{Khachatryan:2014vla}
{\bf ``Identification techniques for highly boosted W bosons that decay into hadrons''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.4227 [hep-ex]
    \\{}10.1007/JHEP12(2014)017
\\{}JHEP {\bf 1412}, 017 (2014) %(Oct 15, 2014)
\href{http://inspirehep.net/record/1322563}{HEP entry}
%18 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014dea}
\item%{Khachatryan:2014dea}
{\bf ``Measurement of electroweak production of two jets in association with a Z boson in proton-proton collisions at $\sqrt{s}=8\,\text {TeV}$''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.3153 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3232-5
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 2, 66 (2015) %(Oct 12, 2014)
\href{http://inspirehep.net/record/1321687}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014jya}
\item%{Khachatryan:2014jya}
{\bf ``Searches for heavy Higgs bosons in two-Higgs-doublet models and for $t→ch$ decay using multilepton and diphoton final states in $pp$ collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.2751 [hep-ex]
    \\{}10.1103/PhysRevD.90.112013
\\{}Phys.\ Rev.\ D {\bf 90}, 112013 (2014) %(Oct 10, 2014)
\href{http://inspirehep.net/record/1321537}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014bva}
\item%{Khachatryan:2014bva}
{\bf ``Measurement of Prompt $\psi(2S) \to J/\psi$ Yield Ratios in Pb-Pb and $p-p$ Collisions at $\sqrt {s_{NN}}=$ 2.76  TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.1804 [nucl-ex]
    \\{}10.1103/PhysRevLett.113.262301
\\{}Phys.\ Rev.\ Lett.\  {\bf 113}, no. 26, 262301 (2014) %(Oct 7, 2014)
\href{http://inspirehep.net/record/1320775}{HEP entry}
%7 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014vma}
\item%{Khachatryan:2014vma}
{\bf ``Measurement of the W boson helicity in events with a single reconstructed top quark in pp collisions at $ \sqrt{s}=8 $ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.1154 [hep-ex]
    \\{}10.1007/JHEP01(2015)053
\\{}JHEP {\bf 1501}, 053 (2015) %(Oct 5, 2014)
\href{http://inspirehep.net/record/1320561}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014uma}
\item%{Khachatryan:2014uma}
{\bf ``Search for Monotop Signatures in Proton-Proton Collisions at $\sqrt s =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1410.1149 [hep-ex]
    \\{}10.1103/PhysRevLett.114.101801
\\{}Phys.\ Rev.\ Lett.\  {\bf 114}, no. 10, 101801 (2015) %(Oct 5, 2014)
\href{http://inspirehep.net/record/1320560}{HEP entry}
%14 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014sca}
\item%{Khachatryan:2014sca}
{\bf ``Search for standard model production of four top quarks in the lepton + jets channel in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1409.7339 [hep-ex]
    \\{}10.1007/JHEP11(2014)154
\\{}JHEP {\bf 1411}, 154 (2014) %(Sep 25, 2014)
\href{http://inspirehep.net/record/1318946}{HEP entry}
%13 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014ofa}
\item%{Khachatryan:2014ofa}
{\bf ``Measurement of the production cross section ratio sigma(chi[b2](1P)) / sigma(chi[b1](1P)) in pp collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1409.5761 [hep-ex]
    \\{}10.1016/j.physletb.2015.02.048
\\{}Phys.\ Lett.\ B {\bf 743}, 383 (2015) %(Sep 19, 2014)
\href{http://inspirehep.net/record/1318344}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014mea}
\item%{Khachatryan:2014mea}
{\bf ``Search for Displaced Supersymmetry in events with an electron and a muon with large impact parameters''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1409.4789 [hep-ex]
    \\{}10.1103/PhysRevLett.114.061801
\\{}Phys.\ Rev.\ Lett.\  {\bf 114}, no. 6, 061801 (2015) %(Sep 16, 2014)
\href{http://inspirehep.net/record/1317640}{HEP entry}
%14 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014jra}
\item%{Khachatryan:2014jra}
{\bf ``Long-range two-particle correlations of strange hadrons with charged particles in pPb and PbPb collisions at LHC energies''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1409.3392 [nucl-ex]
    \\{}10.1016/j.physletb.2015.01.034
\\{}Phys.\ Lett.\ B {\bf 742}, 200 (2015) %(Sep 11, 2014)
\href{http://inspirehep.net/record/1315947}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014mma}
\item%{Khachatryan:2014mma}
{\bf ``Searches for electroweak neutralino and chargino production in channels with Higgs, Z, and W bosons in pp collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1409.3168 [hep-ex]
    \\{}10.1103/PhysRevD.90.092007
\\{}Phys.\ Rev.\ D {\bf 90}, no. 9, 092007 (2014) %(Sep 10, 2014)
\href{http://inspirehep.net/record/1315820}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014rra}
\item%{Khachatryan:2014rra}
{\bf ``Search for dark matter, extra dimensions, and unparticles in monojet events in proton–proton collisions at $\sqrt{s} = 8$ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.3583 [hep-ex]
    \\{}10.1140/epjc/s10052-015-3451-4
\\{}Eur.\ Phys.\ J.\ C {\bf 75}, no. 5, 235 (2015) %(Aug 15, 2014)
\href{http://inspirehep.net/record/1311223}{HEP entry}
%101 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014wca}
\item%{Khachatryan:2014wca}
{\bf ``Search for neutral MSSM Higgs bosons decaying to a pair of tau leptons in pp collisions''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.3316 [hep-ex]
    \\{}10.1007/JHEP10(2014)160
\\{}JHEP {\bf 1410}, 160 (2014) %(Aug 14, 2014)
\href{http://inspirehep.net/record/1310838}{HEP entry}
%80 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014zya}
\item%{Khachatryan:2014zya}
{\bf ``Measurements of jet multiplicity and differential production cross sections of $Z +$ jets events in proton-proton collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.3104 [hep-ex]
    \\{}10.1103/PhysRevD.91.052008
\\{}Phys.\ Rev.\ D {\bf 91}, no. 5, 052008 (2015) %(Aug 13, 2014)
\href{http://inspirehep.net/record/1310737}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014tva}
\item%{Khachatryan:2014tva}
{\bf ``Search for physics beyond the standard model in final states with a lepton and missing transverse energy in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.2745 [hep-ex]
    \\{}10.1103/PhysRevD.91.092005
\\{}Phys.\ Rev.\ D {\bf 91}, no. 9, 092005 (2015) %(Aug 12, 2014)
\href{http://inspirehep.net/record/1310653}{HEP entry}
%59 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014qaa}
\item%{Khachatryan:2014qaa}
{\bf ``Search for the associated production of the Higgs boson with a top-quark pair''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.1682 [hep-ex]
    \\{}10.1007/JHEP09(2014)087, 10.1007/JHEP10(2014)106
\\{}JHEP {\bf 1409}, 087 (2014), [JHEP {\bf 1410}, 106 (2014)] %(Aug 7, 2014)
\href{http://inspirehep.net/record/1310104}{HEP entry}
%60 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014ura}
\item%{Khachatryan:2014ura}
{\bf ``Search for pair production of third-generation scalar leptoquarks and top squarks in proton-proton collisions at sqrt(s) = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1408.0806 [hep-ex]
    \\{}10.1016/j.physletb.2014.10.063
\\{}Phys.\ Lett.\ B {\bf 739}, 229 (2014) %(Aug 4, 2014)
\href{http://inspirehep.net/record/1309874}{HEP entry}
%33 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014loa}
\item%{Khachatryan:2014loa}
{\bf ``Measurement of the $t \bar t$ production cross section in $pp$ collisions at $\sqrt s = 8$ TeV in dilepton final states containing one $\tau$ lepton''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1407.6643 [hep-ex]
    \\{}10.1016/j.physletb.2014.10.032
\\{}Phys.\ Lett.\ B {\bf 739}, 23 (2014) %(Jul 24, 2014)
\href{http://inspirehep.net/record/1307759}{HEP entry}
%10 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014dka}
\item%{Khachatryan:2014dka}
{\bf ``Search for heavy neutrinos and $\mathrm {W}$ bosons with right-handed couplings in proton-proton collisions at $\sqrt{s} = 8\,\text {TeV} $''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1407.3683 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3149-z
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 11, 3149 (2014) %(Jul 14, 2014)
\href{http://inspirehep.net/record/1306295}{HEP entry}
%75 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014xja}
\item%{Khachatryan:2014xja}
{\bf ``Search for new resonances decaying via WZ to leptons in proton-proton collisions at $\sqrt s =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1407.3476 [hep-ex]
    \\{}10.1016/j.physletb.2014.11.026
\\{}Phys.\ Lett.\ B {\bf 740}, 83 (2015) %(Jul 13, 2014)
\href{http://inspirehep.net/record/1306289}{HEP entry}
%29 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014ika}
\item%{Khachatryan:2014ika}
{\bf ``Study of hadronic event-shape variables in multijet final states in pp collisions at sqrt(s) = 7 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1407.2856 [hep-ex]
    \\{}10.1007/JHEP10(2014)087
\\{}JHEP {\bf 1410}, 87 (2014) %(Jul 10, 2014)
\href{http://inspirehep.net/record/1305624}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014ira}
\item%{Khachatryan:2014ira}
{\bf ``Observation of the diphoton decay of the Higgs boson and measurement of its properties''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1407.0558 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3076-z
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 10, 3076 (2014) %(Jul 2, 2014)
\href{http://inspirehep.net/record/1304454}{HEP entry}
%198 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014ewa}
\item%{Khachatryan:2014ewa}
{\bf ``Measurement of top quark-antiquark pair production in association with a W or Z boson in pp collisions at $\sqrt{s} = 8$ $\,\text {TeV}$''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.7830 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3060-7
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 9, 3060 (2014) %(Jun 30, 2014)
\href{http://inspirehep.net/record/1303904}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014uva}
\item%{Khachatryan:2014uva}
{\bf ``Differential cross section measurements for the production of a W boson in association with jets in proton–proton collisions at $\sqrt s=7$ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.7533 [hep-ex]
    \\{}10.1016/j.physletb.2014.12.003
\\{}Phys.\ Lett.\ B {\bf 741}, 12 (2015) %(Jun 29, 2014)
\href{http://inspirehep.net/record/1303894}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014aka}
\item%{Khachatryan:2014aka}
{\bf ``Search for excited quarks in the $\gamma +$jet final state in proton–proton collisions at $\sqrt s=8$ TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.5171 [hep-ex]
    \\{}10.1016/j.physletb.2014.09.048
\\{}Phys.\ Lett.\ B {\bf 738}, 274 (2014) %(Jun 19, 2014)
\href{http://inspirehep.net/record/1301560}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014ava}
\item%{Chatrchyan:2014ava}
{\bf ``Measurement of jet fragmentation in PbPb and pp collisions at $\sqrt{s_{NN}}=2.76$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.0932 [nucl-ex]
    \\{}10.1103/PhysRevC.90.024908
\\{}Phys.\ Rev.\ C {\bf 90}, no. 2, 024908 (2014) %(Jun 3, 2014)
\href{http://inspirehep.net/record/1299142}{HEP entry}
%27 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014iia}
\item%{Khachatryan:2014iia}
{\bf ``Measurement of prompt $J/\psi$ pair production in pp collisions at $ \sqrt{s} $ = 7 Tev''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.0484 [hep-ex]
    \\{}10.1007/JHEP09(2014)094
\\{}JHEP {\bf 1409}, 094 (2014) %(Jun 2, 2014)
\href{http://inspirehep.net/record/1298812}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014gia}
\item%{Chatrchyan:2014gia}
{\bf ``Measurement of the ratio of inclusive jet cross sections using the anti-$k_T$ algorithm with radius parameters R=0.5 and 0.7 in pp collisions at $\sqrt{s}=7$  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.0324 [hep-ex]
    \\{}10.1103/PhysRevD.90.072006
\\{}Phys.\ Rev.\ D {\bf 90}, no. 7, 072006 (2014) %(Jun 2, 2014)
\href{http://inspirehep.net/record/1298810}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2014xja}
\item%{CMS:2014xja}
{\bf ``Measurement of the $pp \to ZZ$ production cross section and constraints on anomalous triple gauge couplings in four-lepton final states at $\sqrt s=$8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1406.0113 [hep-ex]
    \\{}10.1016/j.physletb.2014.11.059
\\{}Phys.\ Lett.\ B {\bf 740}, 250 (2015) %(May 31, 2014)
\href{http://inspirehep.net/record/1298807}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014uwa}
\item%{Khachatryan:2014uwa}
{\bf ``Search for jet extinction in the inclusive jet-$p_t$ spectrum from proton-proton collisions at $\sqrt s =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.7653 [hep-ex]
    \\{}10.1103/PhysRevD.90.032005
\\{}Phys.\ Rev.\ D {\bf 90}, no. 3, 032005 (2014) %(May 29, 2014)
\href{http://inspirehep.net/record/1298512}{HEP entry}
%3 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014qwa}
\item%{Khachatryan:2014qwa}
{\bf ``Searches for electroweak production of charginos, neutralinos, and sleptons decaying to leptons and W, Z, and Higgs bosons in pp collisions at 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.7570 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3036-7
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 9, 3036 (2014) %(May 29, 2014)
\href{http://inspirehep.net/record/1298508}{HEP entry}
%114 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014fsa}
\item%{Chatrchyan:2014fsa}
{\bf ``Measurement of differential cross sections for the production of a pair of isolated photons in pp collisions at $\sqrt{s}=7\,\text {TeV} $''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.7225 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3129-3
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 11, 3129 (2014) %(May 28, 2014)
\href{http://inspirehep.net/record/1298393}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014fea}
\item%{Chatrchyan:2014fea}
{\bf ``Description and performance of track and primary-vertex reconstruction with the CMS tracker''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.6569 [physics.ins-det]
    \\{}10.1088/1748-0221/9/10/P10009
\\{}JINST {\bf 9}, no. 10, P10009 (2014) %(May 26, 2014)
\href{http://inspirehep.net/record/1298029}{HEP entry}
%81 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014goa}
\item%{Chatrchyan:2014goa}
{\bf ``Search for supersymmetry with razor variables in pp collisions at $\sqrt{s}$=7  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.3961 [hep-ex]
    \\{}10.1103/PhysRevD.90.112001
\\{}Phys.\ Rev.\ D {\bf 90}, no. 11, 112001 (2014) %(May 15, 2014)
\href{http://inspirehep.net/record/1296262}{HEP entry}
%13 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014doa}
\item%{Khachatryan:2014doa}
{\bf ``Search for top-squark pairs decaying into Higgs or Z bosons in pp collisions at $\sqrt{s}$=8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.3886 [hep-ex]
    \\{}10.1016/j.physletb.2014.07.053
\\{}Phys.\ Lett.\ B {\bf 736}, 371 (2014) %(May 15, 2014)
\href{http://inspirehep.net/record/1296259}{HEP entry}
%44 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014iha}
\item%{Khachatryan:2014iha}
{\bf ``Constraints on the Higgs boson width from off-shell production and decay to Z-boson pairs''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.3455 [hep-ex]
    \\{}10.1016/j.physletb.2014.06.077
\\{}Phys.\ Lett.\ B {\bf 736}, 64 (2014) %(May 14, 2014)
\href{http://inspirehep.net/record/1296082}{HEP entry}
%93 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014gha}
\item%{Khachatryan:2014gha}
{\bf ``Search for massive resonances decaying into pairs of boosted bosons in semi-leptonic final states at $\sqrt{s} =$ 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.3447 [hep-ex]
    \\{}10.1007/JHEP08(2014)174
\\{}JHEP {\bf 1408}, 174 (2014) %(May 14, 2014)
\href{http://inspirehep.net/record/1296080}{HEP entry}
%72 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014hpa}
\item%{Khachatryan:2014hpa}
{\bf ``Search for massive resonances in dijet systems containing jets tagged as W or Z boson decays in pp collisions at $ \sqrt{s} $ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1405.1994 [hep-ex]
    \\{}10.1007/JHEP08(2014)173
\\{}JHEP {\bf 1408}, 173 (2014) %(May 8, 2014)
\href{http://inspirehep.net/record/1294937}{HEP entry}
%83 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014qka}
\item%{Chatrchyan:2014qka}
{\bf ``Measurement of pseudorapidity distributions of charged particles in proton-proton collisions at $\sqrt{s}$ = 8 TeV by the CMS and TOTEM experiments''}
  \\{}S.~Chatrchyan {\it et al.} [CMS and TOTEM Collaborations].
  \\{}arXiv:1405.0722 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3053-6
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 10, 3053 (2014) %(May 4, 2014)
\href{http://inspirehep.net/record/1294140}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014aea}
\item%{Chatrchyan:2014aea}
{\bf ``Search for anomalous production of events with three or more leptons in $pp$ collisions at $\sqrt(s) =$ 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1404.5801 [hep-ex]
    \\{}10.1103/PhysRevD.90.032006
\\{}Phys.\ Rev.\ D {\bf 90}, 032006 (2014) %(Apr 23, 2014)
\href{http://inspirehep.net/record/1291940}{HEP entry}
%51 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014bza}
\item%{Chatrchyan:2014bza}
{\bf ``Search for $WW \gamma$ and $WZ \gamma$ production and constraints on anomalous quartic gauge couplings in $pp$ collisions at $\sqrt s =$ 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1404.4619 [hep-ex]
    \\{}10.1103/PhysRevD.90.032008
\\{}Phys.\ Rev.\ D {\bf 90}, no. 3, 032008 (2014) %(Apr 17, 2014)
\href{http://inspirehep.net/record/1291135}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014gma}
\item%{Chatrchyan:2014gma}
{\bf ``Measurement of jet multiplicity distributions in $\mathrm {t}\overline{\mathrm {t}}$ production in pp collisions at $\sqrt{s} = 7\,\text {TeV} $''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1404.3171 [hep-ex]
    \\{}10.1140/epjc/s10052-014-3014-0, 10.1140/epjc/s10052-015-3437-2
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, 3014 (2015), [Eur.\ Phys.\ J.\ C {\bf 75}, no. 5, 216 (2015)] %(Apr 11, 2014)
\href{http://inspirehep.net/record/1290126}{HEP entry}
%16 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014nda}
\item%{Khachatryan:2014nda}
{\bf ``Measurement of the ratio $B(t \to Wb)/B(t \to Wq)$ in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1404.2292 [hep-ex]
    \\{}10.1016/j.physletb.2014.06.076
\\{}Phys.\ Lett.\ B {\bf 736}, 33 (2014) %(Apr 8, 2014)
\href{http://inspirehep.net/record/1289223}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014tja}
\item%{Chatrchyan:2014tja}
{\bf ``Search for invisible decays of Higgs bosons in the vector boson fusion and associated ZH production modes''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1404.1344 [hep-ex]
    \\{}10.1140/epjc/s10052-014-2980-6
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, 2980 (2014) %(Apr 4, 2014)
\href{http://inspirehep.net/record/1288709}{HEP entry}
%119 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Khachatryan:2014iya}
\item%{Khachatryan:2014iya}
{\bf ``Measurement of the t-channel single-top-quark production cross section and of the $\mid V_{tb} \mid$ CKM matrix element in pp collisions at $\sqrt{s}$= 8 TeV''}
  \\{}V.~Khachatryan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1403.7366 [hep-ex]
    \\{}10.1007/JHEP06(2014)090
\\{}JHEP {\bf 1406}, 090 (2014) %(Mar 28, 2014)
\href{http://inspirehep.net/record/1287736}{HEP entry}
%51 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014aqa}
\item%{Chatrchyan:2014aqa}
{\bf ``Measurement of WZ and ZZ production in pp collisions at $\sqrt{s} = 8\,\text {TeV} $ in final states with b-tagged jets''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1403.3047 [hep-ex]
    \\{}10.1140/epjc/s10052-014-2973-5
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 8, 2973 (2014) %(Mar 12, 2014)
\href{http://inspirehep.net/record/1285492}{HEP entry}
%16 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014wfa}
\item%{Chatrchyan:2014wfa}
{\bf ``Alignment of the CMS tracker with LHC and cosmic ray data''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1403.2286 [physics.ins-det]
    \\{}10.1088/1748-0221/9/06/P06009
\\{}JINST {\bf 9}, P06009 (2014) %(Mar 10, 2014)
\href{http://inspirehep.net/record/1285228}{HEP entry}
%6 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014lfa}
\item%{Chatrchyan:2014lfa}
{\bf ``Search for new physics in the multijet and missing transverse momentum final state in proton-proton collisions at $\sqrt{s}$= 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1402.4770 [hep-ex]
    \\{}10.1007/JHEP06(2014)055
\\{}JHEP {\bf 1406}, 055 (2014) %(Feb 19, 2014)
\href{http://inspirehep.net/record/1281837}{HEP entry}
%158 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014yta}
\item%{Chatrchyan:2014yta}
{\bf ``Measurements of the $t\bar{t}$ charge asymmetry using the dilepton decay channel in pp collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1402.3803 [hep-ex]
    \\{}10.1007/JHEP04(2014)191
\\{}JHEP {\bf 1404}, 191 (2014) %(Feb 16, 2014)
\href{http://inspirehep.net/record/1281538}{HEP entry}
%28 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014koa}
\item%{Chatrchyan:2014koa}
{\bf ``Search for W' $\to $ tb decays in the lepton + jets final state in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1402.2176 [hep-ex]
    \\{}10.1007/JHEP05(2014)108
\\{}JHEP {\bf 1405}, 108 (2014) %(Feb 10, 2014)
\href{http://inspirehep.net/record/1280718}{HEP entry}
%36 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014dha}
\item%{Chatrchyan:2014dha}
{\bf ``Measurement of the production cross sections for a Z boson and one or more b jets in pp collisions at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1402.1521 [hep-ex]
    \\{}10.1007/JHEP06(2014)120
\\{}JHEP {\bf 1406}, 120 (2014) %(Feb 6, 2014)
\href{http://inspirehep.net/record/1280529}{HEP entry}
%31 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014mua}
\item%{Chatrchyan:2014mua}
{\bf ``Measurement of inclusive W and Z boson production cross sections in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1402.0923 [hep-ex]
    \\{}10.1103/PhysRevLett.112.191802
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, 191802 (2014) %(Feb 4, 2014)
\href{http://inspirehep.net/record/1280200}{HEP entry}
%34 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014vua}
\item%{Chatrchyan:2014vua}
{\bf ``Evidence for the direct decay of the 125 GeV Higgs boson to fermions''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1401.6527 [hep-ex]
    \\{}10.1038/nphys3005
\\{}Nature Phys.\  {\bf 10}, 557 (2014) %(Jan 25, 2014)
\href{http://inspirehep.net/record/1278857}{HEP entry}
%87 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014nva}
\item%{Chatrchyan:2014nva}
{\bf ``Evidence for the 125 GeV Higgs boson decaying to a pair of $\tau$ leptons''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1401.5041 [hep-ex]
    \\{}10.1007/JHEP05(2014)104
\\{}JHEP {\bf 1405}, 104 (2014) %(Jan 20, 2014)
\href{http://inspirehep.net/record/1278199}{HEP entry}
%173 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014hqa}
\item%{Chatrchyan:2014hqa}
{\bf ``Studies of dijet transverse momentum balance and pseudorapidity distributions in pPb collisions at $\sqrt{s_{\mathrm{NN}}} = 5.02$ $\,\text {TeV}$''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1401.4433 [nucl-ex]
    \\{}10.1140/epjc/s10052-014-2951-y
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 7, 2951 (2014) %(Jan 17, 2014)
\href{http://inspirehep.net/record/1278063}{HEP entry}
%38 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2014tua}
\item%{Chatrchyan:2014tua}
{\bf ``Observation of the associated production of a single top quark and a $W$ boson in $pp$ collisions at $\sqrt s = $8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1401.2942 [hep-ex]
    \\{}10.1103/PhysRevLett.112.231802
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, no. 23, 231802 (2014) %(Jan 13, 2014)
\href{http://inspirehep.net/record/1276827}{HEP entry}
%57 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013faa}
\item%{Chatrchyan:2013faa}
{\bf ``Measurement of the $t \bar{t}$ production cross section in the dilepton channel in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.7582 [hep-ex], arXiv:1312.7582
    \\{}10.1007/JHEP02(2014)024, 10.1007/JHEP02(2014)102
\\{}JHEP {\bf 1402}, 024 (2014), [JHEP {\bf 1402}, 102 (2014)] %(Dec 29, 2013)
\href{http://inspirehep.net/record/1275617}{HEP entry}
%63 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013uza}
\item%{Chatrchyan:2013uza}
{\bf ``Measurement of the production cross section for a W boson and two b jets in pp collisions at $\sqrt{s}$=7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.6608 [hep-ex]
    \\{}10.1016/j.physletb.2014.06.041
\\{}Phys.\ Lett.\ B {\bf 735}, 204 (2014) %(Dec 23, 2013)
\href{http://inspirehep.net/record/1273578}{HEP entry}
%18 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013qza}
\item%{Chatrchyan:2013qza}
{\bf ``Measurement of four-jet production in proton-proton collisions at $\sqrt{s}=7$  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.6440 [hep-ex]
    \\{}10.1103/PhysRevD.89.092010
\\{}Phys.\ Rev.\ D {\bf 89}, no. 9, 092010 (2014) %(Dec 22, 2013)
\href{http://inspirehep.net/record/1273574}{HEP entry}
%18 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013nza}
\item%{Chatrchyan:2013nza}
{\bf ``Event activity dependence of Y(nS) production in $\sqrt{s_{NN}}$=5.02 TeV pPb and $\sqrt{s}$=2.76 TeV pp collisions''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.6300 [nucl-ex]
    \\{}10.1007/JHEP04(2014)103
\\{}JHEP {\bf 1404}, 103 (2014) %(Dec 21, 2013)
\href{http://inspirehep.net/record/1273571}{HEP entry}
%24 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mza}
\item%{Chatrchyan:2013mza}
{\bf ``Measurement of the muon charge asymmetry in inclusive $pp \to W+X$ production at $\sqrt s =$ 7 TeV and an improved determination of light parton distribution functions''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.6283 [hep-ex]
    \\{}10.1103/PhysRevD.90.032004
\\{}Phys.\ Rev.\ D {\bf 90}, no. 3, 032004 (2014) %(Dec 21, 2013)
\href{http://inspirehep.net/record/1273570}{HEP entry}
%41 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013xxa}
\item%{Chatrchyan:2013xxa}
{\bf ``Study of double parton scattering using W + 2-jet events in proton-proton collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.5729 [hep-ex]
    \\{}10.1007/JHEP03(2014)032
\\{}JHEP {\bf 1403}, 032 (2014) %(Dec 19, 2013)
\href{http://inspirehep.net/record/1272853}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mxa}
\item%{Chatrchyan:2013mxa}
{\bf ``Measurement of the properties of a Higgs boson in the four-lepton final state''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.5353 [hep-ex]
    \\{}10.1103/PhysRevD.89.092007
\\{}Phys.\ Rev.\ D {\bf 89}, no. 9, 092007 (2014) %(Dec 18, 2013)
\href{http://inspirehep.net/record/1272842}{HEP entry}
%298 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013exa}
\item%{Chatrchyan:2013exa}
{\bf ``Evidence of b-Jet Quenching in PbPb Collisions at $\sqrt{s_{NN}}=2.76$  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.4198 [nucl-ex]
    \\{}10.1103/PhysRevLett.115.029903, 10.1103/PhysRevLett.113.132301
\\{}Phys.\ Rev.\ Lett.\  {\bf 113}, no. 13, 132301 (2014), [Phys.\ Rev.\ Lett.\  {\bf 115}, no. 2, 029903 (2015)] %(Dec 15, 2013)
\href{http://inspirehep.net/record/1269454}{HEP entry}
%33 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013nwa}
\item%{Chatrchyan:2013nwa}
{\bf ``Search for Flavor-Changing Neutral Currents in Top-Quark Decays $t \to Zq$ in $pp$ Collisions at $\sqrt{s}=8$  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.4194 [hep-ex]
    \\{}10.1103/PhysRevLett.112.171802
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, no. 17, 171802 (2014) %(Dec 15, 2013)
\href{http://inspirehep.net/record/1269437}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mya}
\item%{Chatrchyan:2013mya}
{\bf ``Search for top squark and higgsino production using diphoton Higgs boson decays''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.3310 [hep-ex]
    \\{}10.1103/PhysRevLett.112.161802
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, 161802 (2014) %(Dec 11, 2013)
\href{http://inspirehep.net/record/1268812}{HEP entry}
%45 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013wfa}
\item%{Chatrchyan:2013wfa}
{\bf ``Search for top-quark partners with charge 5/3 in the same-sign dilepton final state''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.2391 [hep-ex]
    \\{}10.1103/PhysRevLett.112.171801
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, no. 17, 171801 (2014) %(Dec 9, 2013)
\href{http://inspirehep.net/record/1268328}{HEP entry}
%49 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2013bza}
\item%{CMS:2013bza}
{\bf ``Studies of azimuthal dihadron correlations in ultra-central PbPb collisions at $\sqrt{s_{NN}} =$ 2.76 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.1845 [nucl-ex]
    \\{}10.1007/JHEP02(2014)088
\\{}JHEP {\bf 1402}, 088 (2014) %(Dec 6, 2013)
\href{http://inspirehep.net/record/1268151}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013iaa}
\item%{Chatrchyan:2013iaa}
{\bf ``Measurement of Higgs boson production and properties in the WW decay channel with leptonic final states''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1312.1129 [hep-ex]
    \\{}10.1007/JHEP01(2014)096
\\{}JHEP {\bf 1401}, 096 (2014) %(Dec 4, 2013)
\href{http://inspirehep.net/record/1267508}{HEP entry}
%191 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013uxa}
\item%{Chatrchyan:2013uxa}
{\bf ``Inclusive search for a vector-like T quark with charge $\frac{2}{3}$ in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.7667 [hep-ex]
    \\{}10.1016/j.physletb.2014.01.006
\\{}Phys.\ Lett.\ B {\bf 729}, 149 (2014) %(Nov 29, 2013)
\href{http://inspirehep.net/record/1266766}{HEP entry}
%108 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013fea}
\item%{Chatrchyan:2013fea}
{\bf ``Search for new physics in events with same-sign dileptons and jets in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.6736, arXiv:1311.6736 [hep-ex]
    \\{}10.1007/JHEP01(2015)014, 10.1007/JHEP01(2014)163
\\{}JHEP {\bf 1401}, 163 (2014), [JHEP {\bf 1501}, 014 (2015)] %(Nov 26, 2013)
\href{http://inspirehep.net/record/1266257}{HEP entry}
%83 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mwa}
\item%{Chatrchyan:2013mwa}
{\bf ``Measurement of the triple-differential cross section for photon+jets production in proton-proton collisions at $\sqrt{s}$=7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.6141 [hep-ex]
    \\{}10.1007/JHEP06(2014)009
\\{}JHEP {\bf 1406}, 009 (2014) %(Nov 24, 2013)
\href{http://inspirehep.net/record/1266056}{HEP entry}
%16 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013fha}
\item%{Chatrchyan:2013fha}
{\bf ``Probing color coherence effects in pp collisions at $\sqrt{s}=7\,\text {TeV} $''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.5815 [hep-ex]
    \\{}10.1140/epjc/s10052-014-2901-8
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 6, 2901 (2014) %(Nov 22, 2013)
\href{http://inspirehep.net/record/1265659}{HEP entry}
%8 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013oba}
\item%{Chatrchyan:2013oba}
{\bf ``Search for pair production of excited top quarks in the lepton + jets final state''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.5357 [hep-ex]
    \\{}10.1007/JHEP06(2014)125
\\{}JHEP {\bf 1406}, 125 (2014) %(Nov 21, 2013)
\href{http://inspirehep.net/record/1265512}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013iqa}
\item%{Chatrchyan:2013iqa}
{\bf ``Search for supersymmetry in pp collisions at $\sqrt{s}$=8 TeV in events with a single lepton, large jet multiplicity, and multiple b jets''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.4937 [hep-ex]
    \\{}10.1016/j.physletb.2014.04.023
\\{}Phys.\ Lett.\ B {\bf 733}, 328 (2014) %(Nov 19, 2013)
\href{http://inspirehep.net/record/1265220}{HEP entry}
%63 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013wua}
\item%{Chatrchyan:2013wua}
{\bf ``Measurements of $t\bar{t}$ spin correlations and top-quark polarization using dilepton final states in $pp$ collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.3924 [hep-ex]
    \\{}10.1103/PhysRevLett.112.182001
\\{}Phys.\ Rev.\ Lett.\  {\bf 112}, no. 18, 182001 (2014) %(Nov 15, 2013)
\href{http://inspirehep.net/record/1264662}{HEP entry}
%43 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013gia}
\item%{Chatrchyan:2013gia}
{\bf ``Searches for light- and heavy-flavour three-jet resonances in pp collisions at $\sqrt{s} = 8$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1311.1799 [hep-ex]
    \\{}10.1016/j.physletb.2014.01.049
\\{}Phys.\ Lett.\ B {\bf 730}, 193 (2014) %(Nov 7, 2013)
\href{http://inspirehep.net/record/1263658}{HEP entry}
%28 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013kba}
\item%{Chatrchyan:2013kba}
{\bf ``Measurement of higher-order harmonic azimuthal anisotropy in PbPb collisions at $\sqrt{s_{NN}}$ = 2.76 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.8651 [nucl-ex]
    \\{}10.1103/PhysRevC.89.044906
\\{}Phys.\ Rev.\ C {\bf 89}, no. 4, 044906 (2014) %(Oct 31, 2013)
\href{http://inspirehep.net/record/1262804}{HEP entry}
%44 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013tia}
\item%{Chatrchyan:2013tia}
{\bf ``Measurement of the differential and double-differential Drell-Yan cross sections in proton-proton collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.7291 [hep-ex]
    \\{}10.1007/JHEP12(2013)030
\\{}JHEP {\bf 1312}, 030 (2013) %(Oct 27, 2013)
\href{http://inspirehep.net/record/1262319}{HEP entry}
%41 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013ala}
\item%{Chatrchyan:2013ala}
{\bf ``Jet and underlying event properties as a function of charged-particle multiplicity in proton–proton collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.4554 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2674-5
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 12, 2674 (2013) %(Oct 16, 2013)
\href{http://inspirehep.net/record/1261026}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013zna}
\item%{Chatrchyan:2013zna}
{\bf ``Search for the standard model Higgs boson produced in association with a W or a Z boson and decaying to bottom quarks''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.3687 [hep-ex]
    \\{}10.1103/PhysRevD.89.012003
\\{}Phys.\ Rev.\ D {\bf 89}, no. 1, 012003 (2014) %(Oct 14, 2013)
\href{http://inspirehep.net/record/1258399}{HEP entry}
%176 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013oda}
\item%{Chatrchyan:2013oda}
{\bf ``Rapidity distributions in exclusive Z + jet and $\gamma$ + jet events in $pp$ collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.3082 [hep-ex]
    \\{}10.1103/PhysRevD.88.112009
\\{}Phys.\ Rev.\ D {\bf 88}, no. 11, 112009 (2013) %(Oct 11, 2013)
\href{http://inspirehep.net/record/1258128}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013bba}
\item%{Chatrchyan:2013bba}
{\bf ``Search for baryon number violation in top-quark decays''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.1618 [hep-ex]
    \\{}10.1016/j.physletb.2014.02.033
\\{}Phys.\ Lett.\ B {\bf 731}, 173 (2014) %(Oct 6, 2013)
\href{http://inspirehep.net/record/1257387}{HEP entry}
%4 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013zja}
\item%{Chatrchyan:2013zja}
{\bf ``Measurement of the cross section and angular correlations for associated production of a Z boson with b hadrons in pp collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.1349 [hep-ex]
    \\{}10.1007/JHEP12(2013)039
\\{}JHEP {\bf 1312}, 039 (2013) %(Oct 4, 2013)
\href{http://inspirehep.net/record/1256943}{HEP entry}
%21 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013uja}
\item%{Chatrchyan:2013uja}
{\bf ``Measurement of associated W + charm production in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.1138 [hep-ex]
    \\{}10.1007/JHEP02(2014)013
\\{}JHEP {\bf 1402}, 013 (2014) %(Oct 3, 2013)
\href{http://inspirehep.net/record/1256938}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013kwa}
\item%{Chatrchyan:2013kwa}
{\bf ``Modification of jet shapes in PbPb collisions at $\sqrt {s_{NN}} = 2.76$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1310.0878 [nucl-ex]
    \\{}10.1016/j.physletb.2014.01.042
\\{}Phys.\ Lett.\ B {\bf 730}, 243 (2014) %(Oct 2, 2013)
\href{http://inspirehep.net/record/1256590}{HEP entry}
%49 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013dma}
\item%{Chatrchyan:2013dma}
{\bf ``Observation of a peaking structure in the $J/\psi \phi$ mass spectrum from $B^{\pm} \to J/\psi \phi K^{\pm}$ decays''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1309.6920 [hep-ex]
    \\{}10.1016/j.physletb.2014.05.055
\\{}Phys.\ Lett.\ B {\bf 734}, 261 (2014) %(Sep 26, 2013)
\href{http://inspirehep.net/record/1255647}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013lca}
\item%{Chatrchyan:2013lca}
{\bf ``Searches for new physics using the $t\bar{t}$ invariant mass distribution in pp collisions at $\sqrt{s}$=8  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1309.2030 [hep-ex]
    \\{}10.1103/PhysRevLett.111.211804, 10.1103/PhysRevLett.112.119903
\\{}Phys.\ Rev.\ Lett.\  {\bf 111}, no. 21, 211804 (2013), [Phys.\ Rev.\ Lett.\  {\bf 112}, no. 11, 119903 (2014)] %(Sep 8, 2013)
\href{http://inspirehep.net/record/1253367}{HEP entry}
%60 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013nda}
\item%{Chatrchyan:2013nda}
{\bf ``Measurement of the production cross section for $Z\gamma \to \nu\bar{\nu}\gamma$ in pp collisions at $\sqrt{s} =$ 7 TeV and limits on $ZZ\gamma$ and $Z\gamma\gamma$ triple gauge boson couplings''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1309.1117 [hep-ex]
    \\{}10.1007/JHEP10(2013)164
\\{}JHEP {\bf 1310}, 164 (2013) %(Sep 4, 2013)
\href{http://inspirehep.net/record/1252719}{HEP entry}
%15 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mea}
\item%{Chatrchyan:2013mea}
{\bf ``Search for a new bottomonium state decaying to $\Upsilon(1S)\pi^+\pi^-$ in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1309.0250 [hep-ex]
    \\{}10.1016/j.physletb.2013.10.016
\\{}Phys.\ Lett.\ B {\bf 727}, 57 (2013) %(Sep 1, 2013)
\href{http://inspirehep.net/record/1252068}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013fya}
\item%{Chatrchyan:2013fya}
{\bf ``Measurement of the $W\gamma$ and $Z\gamma$ inclusive cross sections in $pp$ collisions at $\sqrt s=7$  TeV and limits on anomalous triple gauge boson couplings''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1308.6832 [hep-ex]
    \\{}10.1103/PhysRevD.89.092005
\\{}Phys.\ Rev.\ D {\bf 89}, no. 9, 092005 (2014) %(Aug 30, 2013)
\href{http://inspirehep.net/record/1251905}{HEP entry}
%34 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013jna}
\item%{Chatrchyan:2013jna}
{\bf ``Measurement of the W-boson helicity in top-quark decays from $t\bar{t}$ production in lepton+jets events in pp collisions at $\sqrt{s} =$ 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1308.3879 [hep-ex]
    \\{}10.1007/JHEP10(2013)167
\\{}JHEP {\bf 1310}, 167 (2013) %(Aug 18, 2013)
\href{http://inspirehep.net/record/1249595}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013cda}
\item%{Chatrchyan:2013cda}
{\bf ``Angular analysis and branching fraction measurement of the decay $B^0 \to K^{*0} \mu^+\mu^-$''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1308.3409 [hep-ex]
    \\{}10.1016/j.physletb.2013.10.017
\\{}Phys.\ Lett.\ B {\bf 727}, 77 (2013) %(Aug 15, 2013)
\href{http://inspirehep.net/record/1247976}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013xna}
\item%{Chatrchyan:2013xna}
{\bf ``Search for top-squark pair production in the single-lepton final state in pp collisions at $\sqrt{s}$ = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1308.1586 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2677-2
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 12, 2677 (2013) %(Aug 7, 2013)
\href{http://inspirehep.net/record/1246905}{HEP entry}
%190 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013cla}
\item%{Chatrchyan:2013cla}
{\bf ``Measurement of the prompt $J/\psi$ and $\psi$(2S) polarizations in $pp$ collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.6070 [hep-ex]
    \\{}10.1016/j.physletb.2013.10.055
\\{}Phys.\ Lett.\ B {\bf 727}, 381 (2013) %(Jul 23, 2013)
\href{http://inspirehep.net/record/1244128}{HEP entry}
%64 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013vaa}
\item%{Chatrchyan:2013vaa}
{\bf ``Search for a Higgs boson decaying into a Z and a photon in pp collisions at sqrt(s) = 7 and 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.5515 [hep-ex]
    \\{}10.1016/j.physletb.2013.09.057
\\{}Phys.\ Lett.\ B {\bf 726}, 587 (2013) %(Jul 21, 2013)
\href{http://inspirehep.net/record/1243861}{HEP entry}
%92 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013bka}
\item%{Chatrchyan:2013bka}
{\bf ``Measurement of the B(s) to mu+ mu- branching fraction and search for B0 to mu+ mu- with the CMS Experiment''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.5025 [hep-ex]
    \\{}10.1103/PhysRevLett.111.101804
\\{}Phys.\ Rev.\ Lett.\  {\bf 111}, 101804 (2013) %(Jul 18, 2013)
\href{http://inspirehep.net/record/1243425}{HEP entry}
%223 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013xza}
\item%{Chatrchyan:2013xza}
{\bf ``Measurement of the top-quark mass in all-jets $t\bar{t}$ events in pp collisions at $\sqrt{s}$=7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.4617 [hep-ex]
    \\{}10.1140/epjc/s10052-014-2758-x
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 4, 2758 (2014) %(Jul 17, 2013)
\href{http://inspirehep.net/record/1243161}{HEP entry}
%49 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013eya}
\item%{Chatrchyan:2013eya}
{\bf ``Study of the production of charged pions, kaons, and protons in pPb collisions at $\sqrt{s_{NN}} =\  $ 5.02 $\,\text {TeV}$''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.3442 [hep-ex]
    \\{}10.1140/epjc/s10052-014-2847-x
\\{}Eur.\ Phys.\ J.\ C {\bf 74}, no. 6, 2847 (2014) %(Jul 12, 2013)
\href{http://inspirehep.net/record/1242440}{HEP entry}
%61 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013haa}
\item%{Chatrchyan:2013haa}
{\bf ``Determination of the top-quark pole mass and strong coupling constant from the t t-bar production cross section in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1307.1907 [hep-ex]
    \\{}10.1016/j.physletb.2014.08.040, 10.1016/j.physletb.2013.12.009
\\{}Phys.\ Lett.\ B {\bf 728}, 496 (2014), [Phys.\ Lett.\ B {\bf 728}, 526 (2014)] %(Aug 21, 2014)
\href{http://inspirehep.net/record/1241819}{HEP entry}
%81 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013sba}
\item%{Chatrchyan:2013sba}
{\bf ``The performance of the CMS muon detector in proton-proton collisions at sqrt(s) = 7 TeV at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1306.6905 [physics.ins-det]
    \\{}10.1088/1748-0221/8/11/P11002
\\{}JINST {\bf 8}, P11002 (2013) %(Jun 28, 2013)
\href{http://inspirehep.net/record/1240504}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013xsw}
\item%{Chatrchyan:2013xsw}
{\bf ``Search for top squarks in $R$-parity-violating supersymmetry using three or more leptons and b-tagged jets''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1306.6643 [hep-ex]
    \\{}10.1103/PhysRevLett.111.221801
\\{}Phys.\ Rev.\ Lett.\  {\bf 111}, no. 22, 221801 (2013) %(Jun 27, 2013)
\href{http://inspirehep.net/record/1240497}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013dga}
\item%{Chatrchyan:2013dga}
{\bf ``Energy Calibration and Resolution of the CMS Electromagnetic Calorimeter in $pp$ Collisions at $\sqrt{s} = 7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1306.2016 [hep-ex]
    \\{}10.1088/1748-0221/8/09/P09009
\\{}JINST {\bf 8}, P09009 (2013) %(Jun 9, 2013)
\href{http://inspirehep.net/record/1237915}{HEP entry}
%127 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013yaa}
\item%{Chatrchyan:2013yaa}
{\bf ``Measurement of the $W^+W^-$ Cross section in $pp$ Collisions at $\sqrt{s} = 7$ TeV and Limits on Anomalous $WW\gamma$ and $WWZ$ couplings''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1306.1126 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2610-8
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 10, 2610 (2013) %(Jun 5, 2013)
\href{http://inspirehep.net/record/1237104}{HEP entry}
%69 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013jya}
\item%{Chatrchyan:2013jya}
{\bf ``Measurement of the hadronic activity in events with a Z and two jets and extraction of the cross section for the electroweak production of a Z with two jets in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.7389 [hep-ex]
    \\{}10.1007/JHEP10(2013)062
\\{}JHEP {\bf 1310}, 062 (2013) %(May 31, 2013)
\href{http://inspirehep.net/record/1236361}{HEP entry}
%20 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013qsa}
\item%{Chatrchyan:2013qsa}
{\bf ``Measurement of neutral strange particle production in the underlying event in proton-proton collisions at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.6016 [hep-ex]
    \\{}10.1103/PhysRevD.88.052001
\\{}Phys.\ Rev.\ D {\bf 88}, 052001 (2013) %(May 26, 2013)
\href{http://inspirehep.net/record/1235536}{HEP entry}
%6 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013akv}
\item%{Chatrchyan:2013akv}
{\bf ``Study of exclusive two-photon production of $W^+W^-$ in $pp$ collisions at $\sqrt{s} = 7$ TeV and constraints on anomalous quartic gauge couplings''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.5596 [hep-ex]
    \\{}10.1007/JHEP07(2013)116
\\{}JHEP {\bf 1307}, 116 (2013) %(May 23, 2013)
\href{http://inspirehep.net/record/1235421}{HEP entry}
%74 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013wxa}
\item%{Chatrchyan:2013wxa}
{\bf ``Search for gluino mediated bottom- and top-squark production in multijet final states in pp collisions at 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.2390 [hep-ex]
    \\{}10.1016/j.physletb.2013.06.058
\\{}Phys.\ Lett.\ B {\bf 725}, 243 (2013) %(May 10, 2013)
\href{http://inspirehep.net/record/1232968}{HEP entry}
%84 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013nka}
\item%{Chatrchyan:2013nka}
{\bf ``Multiplicity and transverse momentum dependence of two- and four-particle correlations in pPb and PbPb collisions''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.0609 [nucl-ex]
    \\{}10.1016/j.physletb.2013.06.028
\\{}Phys.\ Lett.\ B {\bf 724}, 213 (2013) %(May 2, 2013)
\href{http://inspirehep.net/record/1231945}{HEP entry}
%168 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013oca}
\item%{Chatrchyan:2013oca}
{\bf ``Searches for long-lived charged particles in pp collisions at $\sqrt{s}$=7 and 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1305.0491 [hep-ex]
    \\{}10.1007/JHEP07(2013)122
\\{}JHEP {\bf 1307}, 122 (2013) %(May 2, 2013)
\href{http://inspirehep.net/record/1231738}{HEP entry}
%101 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013txa}
\item%{Chatrchyan:2013txa}
{\bf ``Measurement of the ratio of the inclusive 3-jet cross section to the inclusive 2-jet cross section in pp collisions at $\sqrt{s}$ = 7 TeV and first determination of the strong coupling constant in the TeV range''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1304.7498 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2604-6
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 10, 2604 (2013) %(Apr 28, 2013)
\href{http://inspirehep.net/record/1230937}{HEP entry}
%53 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013sxa}
\item%{Chatrchyan:2013sxa}
{\bf ``Measurement of the $\Lambda_{b}^0$ lifetime in pp collisions at $\sqrt{s} = 7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1304.7495 [hep-ex]
    \\{}10.1007/JHEP07(2013)163
\\{}JHEP {\bf 1307}, 163 (2013) %(Apr 28, 2013)
\href{http://inspirehep.net/record/1230936}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013boa}
\item%{Chatrchyan:2013boa}
{\bf ``Measurement of masses in the $t \bar{t}$ system by kinematic endpoints in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1304.5783 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2494-7
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, 2494 (2013) %(Apr 21, 2013)
\href{http://inspirehep.net/record/1229333}{HEP entry}
%51 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013yoa}
\item%{Chatrchyan:2013yoa}
{\bf ``Search for a standard-model-like Higgs boson with a mass in the range 145 to 1000 GeV at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1304.0213 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2469-8
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, 2469 (2013) %(Mar 31, 2013)
\href{http://inspirehep.net/record/1225976}{HEP entry}
%79 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013yna}
\item%{Chatrchyan:2013yna}
{\bf ``Measurement of the $\Upsilon(1S), \Upsilon(2S)$, and $\Upsilon(3S)$ cross sections in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.5900 [hep-ex]
    \\{}10.1016/j.physletb.2013.10.033
\\{}Phys.\ Lett.\ B {\bf 727}, 101 (2013) %(Mar 23, 2013)
\href{http://inspirehep.net/record/1225274}{HEP entry}
%38 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013xva}
\item%{Chatrchyan:2013xva}
{\bf ``Search for microscopic black holes in pp collisions at sqrt(s) = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.5338 [hep-ex]
    \\{}10.1007/JHEP07(2013)178
\\{}JHEP {\bf 1307}, 178 (2013) %(Mar 21, 2013)
\href{http://inspirehep.net/record/1224805}{HEP entry}
%48 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013vbb}
\item%{Chatrchyan:2013vbb}
{\bf ``Studies of jet mass in dijet and W/Z + jet events''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.4811 [hep-ex]
    \\{}10.1007/JHEP05(2013)090
\\{}JHEP {\bf 1305}, 090 (2013) %(Mar 19, 2013)
\href{http://inspirehep.net/record/1224539}{HEP entry}
%44 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013lba}
\item%{Chatrchyan:2013lba}
{\bf ``Observation of a new boson with mass near 125 GeV in pp collisions at $\sqrt{s}$ = 7 and 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.4571 [hep-ex]
    \\{}10.1007/JHEP06(2013)081
\\{}JHEP {\bf 1306}, 081 (2013) %(Mar 19, 2013)
\href{http://inspirehep.net/record/1224273}{HEP entry}
%350 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012nga}
\item%{CMS:2012nga}
{\bf ``A New Boson with a Mass of 125 GeV Observed with the CMS Experiment at the Large Hadron Collider''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
    \\{}10.1126/science.1230816
\\{}Science {\bf 338}, 1569 (2012). %(2012)
\href{http://inspirehep.net/record/1223729}{HEP entry}
%41 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013qca}
\item%{Chatrchyan:2013qca}
{\bf ``Measurement of associated production of vector bosons and top quark-antiquark pairs at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.3239 [hep-ex]
    \\{}10.1103/PhysRevLett.110.172002
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, 172002 (2013) %(Mar 13, 2013)
\href{http://inspirehep.net/record/1223628}{HEP entry}
%53 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013mys}
\item%{Chatrchyan:2013mys}
{\bf ``Search for supersymmetry in hadronic final states with missing transverse energy using the variables $\alpha_T$ and b-quark multiplicity in pp collisions at $\sqrt s=8$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.2985 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2568-6
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 9, 2568 (2013) %(Mar 12, 2013)
\href{http://inspirehep.net/record/1223519}{HEP entry}
%164 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013yea}
\item%{Chatrchyan:2013yea}
{\bf ``Search for the standard model Higgs boson produced in association with a top-quark pair in pp collisions at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1303.0763 [hep-ex]
    \\{}10.1007/JHEP05(2013)145
\\{}JHEP {\bf 1305}, 145 (2013) %(Mar 4, 2013)
\href{http://inspirehep.net/record/1222336}{HEP entry}
%64 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013qha}
\item%{Chatrchyan:2013qha}
{\bf ``Search for narrow resonances using the dijet mass spectrum in pp collisions at $\sqrt{s}$=8  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.4794 [hep-ex]
    \\{}10.1103/PhysRevD.87.114015
\\{}Phys.\ Rev.\ D {\bf 87}, no. 11, 114015 (2013) %(Feb 19, 2013)
\href{http://inspirehep.net/record/1220378}{HEP entry}
%104 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013cld}
\item%{Chatrchyan:2013cld}
{\bf ``Measurement of the X(3872) production cross section via decays to J/psi pi pi in pp collisions at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.3968 [hep-ex]
    \\{}10.1007/JHEP04(2013)154
\\{}JHEP {\bf 1304}, 154 (2013) %(Feb 16, 2013)
\href{http://inspirehep.net/record/1219950}{HEP entry}
%60 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013qga}
\item%{Chatrchyan:2013qga}
{\bf ``Search for a Higgs boson decaying into a b-quark pair and produced in association with b quarks in proton-proton collisions at 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.2892 [hep-ex]
    \\{}10.1016/j.physletb.2013.04.017
\\{}Phys.\ Lett.\ B {\bf 722}, 207 (2013) %(Feb 12, 2013)
\href{http://inspirehep.net/record/1219000}{HEP entry}
%55 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013lga}
\item%{Chatrchyan:2013lga}
{\bf ``Search for new physics in final states with a lepton and missing transverse energy in pp collisions at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.2812 [hep-ex]
    \\{}10.1103/PhysRevD.87.072005
\\{}Phys.\ Rev.\ D {\bf 87}, no. 7, 072005 (2013) %(Feb 12, 2013)
\href{http://inspirehep.net/record/1218995}{HEP entry}
%36 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013gfi}
\item%{Chatrchyan:2013gfi}
{\bf ``Study of the underlying event at forward rapidity in pp collisions at $\sqrt{s}$ = 0.9, 2.76, and 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.2394 [hep-ex]
    \\{}10.1007/JHEP04(2013)072
\\{}JHEP {\bf 1304}, 072 (2013) %(Feb 10, 2013)
\href{http://inspirehep.net/record/1218372}{HEP entry}
%36 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013sfs}
\item%{Chatrchyan:2013sfs}
{\bf ``Searches for Higgs bosons in pp collisions at sqrt(s) = 7 and 8 TeV in the context of four-generation and fermiophobic models''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.1764 [hep-ex]
    \\{}10.1016/j.physletb.2013.06.043
\\{}Phys.\ Lett.\ B {\bf 725}, 36 (2013) %(Feb 7, 2013)
\href{http://inspirehep.net/record/1218021}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013izb}
\item%{Chatrchyan:2013izb}
{\bf ``Search for pair-produced dijet resonances in four-jet final states in pp collisions at $\sqrt{s}$=7  TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.0531 [hep-ex]
    \\{}10.1103/PhysRevLett.110.141802
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, no. 14, 141802 (2013) %(Feb 3, 2013)
\href{http://inspirehep.net/record/1217552}{HEP entry}
%41 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013ual}
\item%{Chatrchyan:2013ual}
{\bf ``Measurement of the $t\bar{t}$ production cross section in the all-jet final state in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1302.0508 [hep-ex]
    \\{}10.1007/JHEP05(2013)065
\\{}JHEP {\bf 1305}, 065 (2013) %(Feb 3, 2013)
\href{http://inspirehep.net/record/1217551}{HEP entry}
%30 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013kff}
\item%{Chatrchyan:2013kff}
{\bf ``Measurement of the top-antitop production cross section in the tau+jets channel in pp collisions at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.5755 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2386-x
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 4, 2386 (2013) %(Jan 24, 2013)
\href{http://inspirehep.net/record/1216035}{HEP entry}
%30 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013muj}
\item%{Chatrchyan:2013muj}
{\bf ``Search for contact interactions using the inclusive jet $p_T$ spectrum in $pp$ collisions at $\sqrt{s} = 7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.5023 [hep-ex]
    \\{}10.1103/PhysRevD.87.052017
\\{}Phys.\ Rev.\ D {\bf 87}, no. 5, 052017 (2013) %(Jan 21, 2013)
\href{http://inspirehep.net/record/1215599}{HEP entry}
%24 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013oev}
\item%{Chatrchyan:2013oev}
{\bf ``Measurement of W+W- and ZZ production cross sections in pp collisions at sqrt(s) = 8 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.4698 [hep-ex]
    \\{}10.1016/j.physletb.2013.03.027
\\{}Phys.\ Lett.\ B {\bf 721}, 190 (2013) %(Jan 20, 2013)
\href{http://inspirehep.net/record/1215317}{HEP entry}
%118 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013dsa}
\item%{Chatrchyan:2013dsa}
{\bf ``Search for physics beyond the standard model in events with $\tau$ leptons, jets, and large transverse momentum imbalance in pp collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.3792 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2493-8
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, 2493 (2013) %(Jan 2013)
\href{http://inspirehep.net/record/1211187}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013sza}
\item%{Chatrchyan:2013sza}
{\bf ``Interpretation of Searches for Supersymmetry with simplified Models''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.2175 [hep-ex]
    \\{}10.1103/PhysRevD.88.052017
\\{}Phys.\ Rev.\ D {\bf 88}, no. 5, 052017 (2013) %(Jan 2013)
\href{http://inspirehep.net/record/1210032}{HEP entry}
%74 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013tna}
\item%{Chatrchyan:2013tna}
{\bf ``Event shapes and azimuthal correlations in $Z$ + jets events in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.1646 [hep-ex]
    \\{}10.1016/j.physletb.2013.04.025
\\{}Phys.\ Lett.\ B {\bf 722}, 238 (2013) %(Jan 2013)
\href{http://inspirehep.net/record/1209721}{HEP entry}
%36 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2013kha}
\item%{Chatrchyan:2013kha}
{\bf ``Search for supersymmetry in events with opposite-sign dileptons and missing transverse energy using an artificial neural network''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1301.0916 [hep-ex]
    \\{}10.1103/PhysRevD.87.072001
\\{}Phys.\ Rev.\ D {\bf 87}, no. 7, 072001 (2013) %(Jan 2013)
\href{http://inspirehep.net/record/1209556}{HEP entry}
%11 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012yxr}
\item%{Chatrchyan:2012yxr}
{\bf ``Search for supersymmetry in $pp$ collisions at $\sqrt{s}=7$ TeV in events with a single lepton, jets, and missing transverse momentum''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6428 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2404-z
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, 2404 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208988}{HEP entry}
%20 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012jja}
\item%{Chatrchyan:2012jja}
{\bf ``Study of the Mass and Spin-Parity of the Higgs Boson Candidate Via Its Decays to Z Boson Pairs''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6639 [hep-ex]
    \\{}10.1103/PhysRevLett.110.081803
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, no. 8, 081803 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208931}{HEP entry}
%259 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012bja}
\item%{Chatrchyan:2012bja}
{\bf ``Measurements of differential jet cross sections in proton-proton collisions at $\sqrt{s}=7$ TeV with the CMS detector''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6660 [hep-ex]
    \\{}10.1103/PhysRevD.87.112002, 10.1103/PhysRevD.87.119902
\\{}Phys.\ Rev.\ D {\bf 87}, no. 11, 112002 (2013), [Phys.\ Rev.\ D {\bf 87}, no. 11, 119902 (2013)] %(Dec 2012)
\href{http://inspirehep.net/record/1208923}{HEP entry}
%101 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ria}
\item%{Chatrchyan:2012ria}
{\bf ``Measurement of the $t\bar{t}$ production cross section in $pp$ collisions at $\sqrt{s}=7$ TeV with lepton + jets final states''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6682
    \\{}10.1016/j.physletb.2013.02.021
\\{}Phys.\ Lett.\ B {\bf 720}, 83 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208913}{HEP entry}
%54 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012uea}
\item%{Chatrchyan:2012uea}
{\bf ``Inclusive search for supersymmetry using the razor variables in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6961 [hep-ex]
    \\{}10.1103/PhysRevLett.111.081802
\\{}Phys.\ Rev.\ Lett.\  {\bf 111}, no. 8, 081802 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208812}{HEP entry}
%59 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012paa}
\item%{Chatrchyan:2012paa}
{\bf ``Search for new physics in events with same-sign dileptons and $b$ jets in $pp$ collisions at $\sqrt{s}=8$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6194 [hep-ex]
    \\{}10.1007/JHEP03(2013)037, 10.1007/JHEP07(2013)041
\\{}JHEP {\bf 1303}, 037 (2013), [JHEP {\bf 1307}, 041 (2013)] %(Dec 2012)
\href{http://inspirehep.net/record/1208703}{HEP entry}
%75 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012oaa}
\item%{Chatrchyan:2012oaa}
{\bf ``Search for heavy narrow dilepton resonances in $pp$ collisions at $\sqrt{s}=7$ TeV and $\sqrt{s}=8$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.6175 [hep-ex]
    \\{}10.1016/j.physletb.2013.02.003
\\{}Phys.\ Lett.\ B {\bf 720}, 63 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208702}{HEP entry}
%96 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012hda}
\item%{Chatrchyan:2012hda}
{\bf ``Search for contact interactions in $\mu^+\mu^-$ events in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.4563 [hep-ex]
    \\{}10.1103/PhysRevD.87.032001
\\{}Phys.\ Rev.\ D {\bf 87}, no. 3, 032001 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1208097}{HEP entry}
%15 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ypy}
\item%{Chatrchyan:2012ypy}
{\bf ``Search for heavy resonances in the W/Z-tagged dijet mass spectrum in pp collisions at 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.1910 [hep-ex]
    \\{}10.1016/j.physletb.2013.05.040
\\{}Phys.\ Lett.\ B {\bf 723}, 280 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1206606}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012jwg}
\item%{Chatrchyan:2012jwg}
{\bf ``Search for long-lived particles decaying to photons and missing energy in proton-proton collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1212.1838 [hep-ex]
    \\{}10.1016/j.physletb.2013.04.027
\\{}Phys.\ Lett.\ B {\bf 722}, 273 (2013) %(Dec 2012)
\href{http://inspirehep.net/record/1206603}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012rva}
\item%{Chatrchyan:2012rva}
{\bf ``Search for exotic resonances decaying into $WZ/ZZ$ in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.5779 [hep-ex]
    \\{}10.1007/JHEP02(2013)036
\\{}JHEP {\bf 1302}, 036 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1203843}{HEP entry}
%24 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012sga}
\item%{Chatrchyan:2012sga}
{\bf ``Measurement of the $ZZ$ production cross section and search for anomalous couplings in 2 l2l ' final states in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.4890 [hep-ex]
    \\{}10.1007/JHEP01(2013)063
\\{}JHEP {\bf 1301}, 063 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1203454}{HEP entry}
%59 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012bba}
\item%{Chatrchyan:2012bba}
{\bf ``Search for new physics in events with photons, jets, and missing transverse energy in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.4784 [hep-ex]
    \\{}10.1007/JHEP03(2013)111
\\{}JHEP {\bf 1303}, 111 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1203307}{HEP entry}
%36 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012jua}
\item%{Chatrchyan:2012jua}
{\bf ``Identification of b-quark jets with the CMS experiment''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.4462 [hep-ex]
    \\{}10.1088/1748-0221/8/04/P04013
\\{}JINST {\bf 8}, P04013 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1203133}{HEP entry}
%338 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012yca}
\item%{Chatrchyan:2012yca}
{\bf ``Search for $Z$ ' resonances decaying to $t\bar{t}$ in dilepton+jets final states in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.3338 [hep-ex]
    \\{}10.1103/PhysRevD.87.072002
\\{}Phys.\ Rev.\ D {\bf 87}, no. 7, 072002 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1202680}{HEP entry}
%45 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012sca}
\item%{Chatrchyan:2012sca}
{\bf ``Search for supersymmetry in final states with a single lepton, $b$-quark jets, and missing transverse energy in proton-proton collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.3143 [hep-ex]
    \\{}10.1103/PhysRevD.87.052006
\\{}Phys.\ Rev.\ D {\bf 87}, no. 5, 052006 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1202674}{HEP entry}
%22 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012jna}
\item%{Chatrchyan:2012jna}
{\bf ``Search in leptonic channels for heavy resonances decaying to long-lived neutral particles''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.2472 [hep-ex]
    \\{}10.1007/JHEP02(2013)085
\\{}JHEP {\bf 1302}, 085 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1202275}{HEP entry}
%39 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012saa}
\item%{Chatrchyan:2012saa}
{\bf ``Measurement of differential top-quark pair production cross sections in $pp$ colisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1211.2220 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2339-4
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 3, 2339 (2013) %(Nov 2012)
\href{http://inspirehep.net/record/1201946}{HEP entry}
%128 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012wa}
\item%{Chatrchyan:2012wa}
{\bf ``Search for supersymmetry in final states with missing transverse energy and 0, 1, 2, or at least 3 b-quark jets in 7 TeV pp collisions using the variable alphaT''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.8115 [hep-ex]
    \\{}10.1007/JHEP01(2013)077
\\{}JHEP {\bf 1301}, 077 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1194120}{HEP entry}
%57 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012cg}
\item%{Chatrchyan:2012cg}
{\bf ``Search for a non-standard-model Higgs boson decaying to a pair of new light bosons in four-muon final states''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.7619 [hep-ex]
    \\{}10.1016/j.physletb.2013.09.009
\\{}Phys.\ Lett.\ B {\bf 726}, 564 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1193937}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012bd}
\item%{Chatrchyan:2012bd}
{\bf ``Measurement of the sum of $W W$ and $WZ$ production with $W+$dijet events in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.7544 [hep-ex]
    \\{}10.1140/epjc/s10052-013-2283-3
\\{}Eur.\ Phys.\ J.\ C {\bf 73}, no. 2, 2283 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1193935}{HEP entry}
%60 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012af}
\item%{Chatrchyan:2012af}
{\bf ``Search for heavy quarks decaying into a top quark and a $W$ or $Z$ boson using lepton + jets events in $pp$ collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.7471 [hep-ex]
    \\{}10.1007/JHEP01(2013)154
\\{}JHEP {\bf 1301}, 154 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1193934}{HEP entry}
%40 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012nj}
\item%{Chatrchyan:2012nj}
{\bf ``Measurement of the inelastic proton-proton cross section at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.6718 [hep-ex]
    \\{}10.1016/j.physletb.2013.03.024
\\{}Phys.\ Lett.\ B {\bf 722}, 5 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1193338}{HEP entry}
%67 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012sv}
\item%{Chatrchyan:2012sv}
{\bf ``Search for pair production of third-generation leptoquarks and top squarks in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.5629 [hep-ex]
    \\{}10.1103/PhysRevLett.110.081801
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, no. 8, 081801 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1192034}{HEP entry}
%44 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012st}
\item%{Chatrchyan:2012st}
{\bf ``Search for third-generation leptoquarks and scalar bottom quarks in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.5627 [hep-ex]
    \\{}10.1007/JHEP12(2012)055
\\{}JHEP {\bf 1212}, 055 (2012) %(Oct 2012)
\href{http://inspirehep.net/record/1192033}{HEP entry}
%28 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012qk}
\item%{CMS:2012qk}
{\bf ``Observation of long-range near-side angular correlations in proton-lead collisions at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.5482 [nucl-ex]
    \\{}10.1016/j.physletb.2012.11.025
\\{}Phys.\ Lett.\ B {\bf 718}, 795 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1191899}{HEP entry}
%235 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012ad}
\item%{CMS:2012ad}
{\bf ``Search for excited leptons in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.2422 [hep-ex]
    \\{}10.1016/j.physletb.2013.02.031
\\{}Phys.\ Lett.\ B {\bf 720}, 309 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1189987}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012zv}
\item%{CMS:2012zv}
{\bf ``Search for heavy neutrinos and W[R] bosons with right-handed couplings in a left-right symmetric model in pp collisions at sqrt(s) = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.2402 [hep-ex]
    \\{}10.1103/PhysRevLett.109.261802
\\{}Phys.\ Rev.\ Lett.\  {\bf 109}, 261802 (2012) %(Oct 2012)
\href{http://inspirehep.net/record/1189986}{HEP entry}
%29 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012yf}
\item%{CMS:2012yf}
{\bf ``Search for narrow resonances and quantum black holes in inclusive and $b$-tagged dijet mass spectra from $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.2387 [hep-ex]
    \\{}10.1007/JHEP01(2013)013
\\{}JHEP {\bf 1301}, 013 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1189823}{HEP entry}
%46 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012xi}
\item%{CMS:2012xi}
{\bf ``Search for fractionally charged particles in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.2311 [hep-ex]
    \\{}10.1103/PhysRevD.87.092008
\\{}Phys.\ Rev.\ D {\bf 87}, no. 9, 092008 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1189819}{HEP entry}
%14 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012un}
\item%{CMS:2012un}
{\bf ``Search for supersymmetry in events with photons and low missing transverse energy in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.2052 [hep-ex]
    \\{}10.1016/j.physletb.2012.12.055
\\{}Phys.\ Lett.\ B {\bf 719}, 42 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1189815}{HEP entry}
%26 citations counted in INSPIRE as of 21 sept. 2015


%\cite{CMS:2012ra}
\item%{CMS:2012ra}
{\bf ``Search for heavy lepton partners of neutrinos in proton-proton collisions in the context of the type III seesaw mechanism''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.1797 [hep-ex]
    \\{}10.1016/j.physletb.2012.10.070
\\{}Phys.\ Lett.\ B {\bf 718}, 348 (2012) %(Oct 2012)
\href{http://inspirehep.net/record/1189663}{HEP entry}
%30 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ub}
\item%{Chatrchyan:2012ub}
{\bf ``Measurement of the relative prompt production rate of chi(c2) and chi(c1) in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.0875 [hep-ex]
    \\{}10.1140/epjc/s10052-012-2251-3
\\{}Eur.\ Phys.\ J.\ C {\bf 72}, 2251 (2012) %(Oct 2012)
\href{http://inspirehep.net/record/1189050}{HEP entry}
%38 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012tw}
\item%{Chatrchyan:2012tw}
{\bf ``Search for anomalous production of highly boosted $Z$ bosons decaying to dimuons in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1210.0867 [hep-ex]
    \\{}10.1016/j.physletb.2013.03.037
\\{}Phys.\ Lett.\ B {\bf 722}, 28 (2013) %(Oct 2012)
\href{http://inspirehep.net/record/1189049}{HEP entry}
%9 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012pka}
\item%{Chatrchyan:2012pka}
{\bf ``Search for electroweak production of charginos and neutralinos using leptonic final states in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.6620 [hep-ex]
    \\{}10.1007/JHEP11(2012)147
\\{}JHEP {\bf 1211}, 147 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1188683}{HEP entry}
%65 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ep}
\item%{Chatrchyan:2012ep}
{\bf ``Measurement of the single-top-quark $t$-channel cross section in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.4533 [hep-ex]
    \\{}10.1007/JHEP12(2012)035
\\{}JHEP {\bf 1212}, 035 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1186734}{HEP entry}
%129 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012cx}
\item%{Chatrchyan:2012cx}
{\bf ``Search for resonant $t\bar{t}$ production in lepton+jets events in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.4397 [hep-ex]
    \\{}10.1007/JHEP12(2012)015
\\{}JHEP {\bf 1212}, 015 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1186730}{HEP entry}
%51 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012qr}
\item%{Chatrchyan:2012qr}
{\bf ``Search for the standard model Higgs boson produced in association with $W$ and $Z$ bosons in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.3937 [hep-ex]
    \\{}10.1007/JHEP11(2012)088
\\{}JHEP {\bf 1211}, 088 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1186385}{HEP entry}
%10 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012baa}
\item%{Chatrchyan:2012baa}
{\bf ``Search for a narrow spin-2 resonance decaying to a pair of Z vector bosons in the semileptonic final state''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.3807 [hep-ex]
    \\{}10.1016/j.physletb.2012.11.063
\\{}Phys.\ Lett.\ B {\bf 718}, 1208 (2013) %(Sep 2012)
\href{http://inspirehep.net/record/1186381}{HEP entry}
%17 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012zca}
\item%{Chatrchyan:2012zca}
{\bf ``Evidence for associated production of a single top quark and W boson in $pp$ collisions at $\sqrt{s}$ = 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.3489 [hep-ex]
    \\{}10.1103/PhysRevLett.110.022003
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, 022003 (2013) %(Sep 2012)
\href{http://inspirehep.net/record/1185781}{HEP entry}
%90 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012woa}
\item%{Chatrchyan:2012woa}
{\bf ``Measurement of the $Y(1S), Y(2S)$ and $Y(3S)$ polarizations in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.2922 [hep-ex]
    \\{}10.1103/PhysRevLett.110.081802
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, no. 8, 081802 (2013) %(Sep 2012)
\href{http://inspirehep.net/record/1185414}{HEP entry}
%82 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ea}
\item%{Chatrchyan:2012ea}
{\bf ``Measurement of the top-quark mass in $t\bar{t}$ events with dilepton final states in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.2393 [hep-ex]
    \\{}10.1140/epjc/s10052-012-2202-z
\\{}Eur.\ Phys.\ J.\ C {\bf 72}, 2202 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1185104}{HEP entry}
%67 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012cz}
\item%{Chatrchyan:2012cz}
{\bf ``Measurement of the top-quark mass in $t\bar{t}$ events with lepton+jets final states in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.2319 [hep-ex]
    \\{}10.1007/JHEP12(2012)105
\\{}JHEP {\bf 1212}, 105 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1185101}{HEP entry}
%83 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012vc}
\item%{Chatrchyan:2012vc}
{\bf ``Observation of a diffractive contribution to dijet production in proton-proton collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.1805 [hep-ex]
    \\{}10.1103/PhysRevD.87.012006
\\{}Phys.\ Rev.\ D {\bf 87}, no. 1, 012006 (2013) %(Sep 2012)
\href{http://inspirehep.net/record/1184941}{HEP entry}
%24 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012fp}
\item%{Chatrchyan:2012fp}
{\bf ``Combined search for the quarks of a sequential fourth generation''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.1062 [hep-ex]
    \\{}10.1103/PhysRevD.86.112003
\\{}Phys.\ Rev.\ D {\bf 86}, 112003 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1184487}{HEP entry}
%37 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012vu}
\item%{Chatrchyan:2012vu}
{\bf ``Search for pair produced fourth-generation up-type quarks in $pp$ collisions at $\sqrt{s}=7$ TeV with a lepton in the final state''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1209.0471 [hep-ex]
    \\{}10.1016/j.physletb.2012.10.038
\\{}Phys.\ Lett.\ B {\bf 718}, 307 (2012) %(Sep 2012)
\href{http://inspirehep.net/record/1184341}{HEP entry}
%55 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012rg}
\item%{Chatrchyan:2012rg}
{\bf ``Search for supersymmetry in events with b-quark jets and missing transverse energy in pp collisions at 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.4859 [hep-ex]
    \\{}10.1103/PhysRevD.86.072010
\\{}Phys.\ Rev.\ D {\bf 86}, 072010 (2012) %(Aug 2012)
\href{http://inspirehep.net/record/1181767}{HEP entry}
%35 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012jra}
\item%{Chatrchyan:2012jra}
{\bf ``Study of the dijet mass spectrum in $pp \to W +$ jets events at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.3477 [hep-ex]
    \\{}10.1103/PhysRevLett.109.251801
\\{}Phys.\ Rev.\ Lett.\  {\bf 109}, 251801 (2012) %(Aug 2012)
\href{http://inspirehep.net/record/1128019}{HEP entry}
%21 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012uxa}
\item%{Chatrchyan:2012uxa}
{\bf ``Search for three-jet resonances in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.2931 [hep-ex]
    \\{}10.1016/j.physletb.2012.10.048
\\{}Phys.\ Lett.\ B {\bf 718}, 329 (2012) %(Aug 2012)
\href{http://inspirehep.net/record/1127510}{HEP entry}
%39 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012lxa}
\item%{Chatrchyan:2012lxa}
{\bf ``Observation of sequential Upsilon suppression in PbPb collisions''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.2826 [nucl-ex]
    \\{}10.1103/PhysRevLett.109.222301
\\{}Phys.\ Rev.\ Lett.\  {\bf 109}, 222301 (2012) %(Aug 2012)
\href{http://inspirehep.net/record/1127501}{HEP entry}
%138 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012bra}
\item%{Chatrchyan:2012bra}
{\bf ``Measurement of the $t\bar{t}$ production cross section in the dilepton channel in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.2671 [hep-ex]
    \\{}10.1007/JHEP11(2012)067
\\{}JHEP {\bf 1211}, 067 (2012) %(Aug 2012)
\href{http://inspirehep.net/record/1127335}{HEP entry}
%129 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012vqa}
\item%{Chatrchyan:2012vqa}
{\bf ``Measurement of the azimuthal anisotropy of neutral pions in PbPb collisions at $\sqrt{s_{NN}}=2.76$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.2470 [nucl-ex]
    \\{}10.1103/PhysRevLett.110.042301
\\{}Phys.\ Rev.\ Lett.\  {\bf 110}, no. 4, 042301 (2013) %(Aug 2012)
\href{http://inspirehep.net/record/1127329}{HEP entry}
%19 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012hqa}
\item%{Chatrchyan:2012hqa}
{\bf ``Search for flavor changing neutral currents in top quark decays in pp collisions at 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1208.0957 [hep-ex]
    \\{}10.1016/j.physletb.2012.12.045
\\{}Phys.\ Lett.\ B {\bf 718}, 1252 (2013) %(Aug 2012)
\href{http://inspirehep.net/record/1125963}{HEP entry}
%44 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012xdj}
\item%{Chatrchyan:2012xdj}
{\bf ``Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.7235 [hep-ex]
    \\{}10.1016/j.physletb.2012.08.021
\\{}Phys.\ Lett.\ B {\bf 716}, 30 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1124338}{HEP entry}
%4841 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012fla}
\item%{Chatrchyan:2012fla}
{\bf ``Search for heavy Majorana neutrinos in $\mu^+\mu^+[\mu^-\mu^-]$ and $e^+e^+[e^-e^-]$ events in $pp$ collisions at $\sqrt{s} = 7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.6079 [hep-ex]
    \\{}10.1016/j.physletb.2012.09.012
\\{}Phys.\ Lett.\ B {\bf 717}, 109 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1123803}{HEP entry}
%42 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012vza}
\item%{Chatrchyan:2012vza}
{\bf ``Search for pair production of first- and second-generation scalar leptoquarks in $pp$ collisions at $\sqrt{s}= 7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.5406 [hep-ex]
    \\{}10.1103/PhysRevD.86.052013
\\{}Phys.\ Rev.\ D {\bf 86}, 052013 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1123507}{HEP entry}
%50 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012qb}
\item%{Chatrchyan:2012qb}
{\bf ``Study of the inclusive production of charged pions, kaons, and protons in $pp$ collisions at $\sqrt{s}=0.9$, 2.76, and 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.4724 [hep-ex]
    \\{}10.1140/epjc/s10052-012-2164-1
\\{}Eur.\ Phys.\ J.\ C {\bf 72}, 2164 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1123117}{HEP entry}
%70 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012ir}
\item%{Chatrchyan:2012ir}
{\bf ``Search for new physics with long-lived particles decaying to photons and missing energy in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.0627 [hep-ex]
    \\{}10.1007/JHEP11(2012)172
\\{}JHEP {\bf 1211}, 172 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1120997}{HEP entry}
%12 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012cxa}
\item%{Chatrchyan:2012cxa}
{\bf ``Inclusive and differential measurements of the $t \bar{t}$ charge asymmetry in proton-proton collisions at 7 TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1207.0065 [hep-ex]
    \\{}10.1016/j.physletb.2012.09.028
\\{}Phys.\ Lett.\ B {\bf 717}, 129 (2012) %(Jul 2012)
\href{http://inspirehep.net/record/1120732}{HEP entry}
%93 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012am}
\item%{Chatrchyan:2012am}
{\bf ``Search for a light pseudoscalar Higgs boson in the dimuon decay channel in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1206.6326 [hep-ex]
    \\{}10.1103/PhysRevLett.109.121801
\\{}Phys.\ Rev.\ Lett.\  {\bf 109}, 121801 (2012) %(Jun 2012)
\href{http://inspirehep.net/record/1120142}{HEP entry}
%45 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012me}
\item%{Chatrchyan:2012me}
{\bf ``Search for dark matter and large extra dimensions in monojet events in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1206.5663 [hep-ex]
    \\{}10.1007/JHEP09(2012)094
\\{}JHEP {\bf 1209}, 094 (2012) %(Jun 2012)
\href{http://inspirehep.net/record/1119567}{HEP entry}
%209 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012kk}
\item%{Chatrchyan:2012kk}
{\bf ``Search for a $W^\prime$ or Techni-$\rho$ Decaying into $WZ$ in $pp$ Collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1206.0433 [hep-ex]
    \\{}10.1103/PhysRevLett.109.141801
\\{}Phys.\ Rev.\ Lett.\  {\bf 109}, 141801 (2012) %(Jun 2012)
\href{http://inspirehep.net/record/1117012}{HEP entry}
%38 citations counted in INSPIRE as of 21 sept. 2015


%\cite{Chatrchyan:2012vca}
\item%{Chatrchyan:2012vca}
{\bf ``Search for a light charged Higgs boson in top quark decays in $pp$ collisions at $\sqrt{s}=7$ TeV''}
  \\{}S.~Chatrchyan {\it et al.} [CMS Collaboration].
  \\{}arXiv:1205.5736 [hep-ex]
    \\{}10.1007/JHEP07(2012)143
\\{}JHEP {\bf 1207}, 143 (2012) %(May 2012)
\href{http://inspirehep.net/record/1116149}{HEP entry}
%168 citations counted in INSPIRE as of 21 sept. 2015


\end{enumerate}
\end{document}
